---
title: "clogit"
output: html_document
---

## Summary
Running Conditional Logit Analysis on the following models to compare output and explore potential bias; Standard opt-out model (Model I), Pooled (Model II), Unforced Responses (Model III), and Forced Responses (Model IV).
 
## Data Source 
Personal Interviews
 
## Reference 
Panga Watch
 
## Downloaded
October 21, 2019
 
Time range: 
2019
 
## Format
comma separated values

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(survival)
library(AlgDesign)
library(DT)
library(stargazer)
library(xtable)
library(here)
library(kableExtra)
#library("mlogit")
```

Standard opt-out model (Model I)
```{r}
standard_opt_out <- read_csv("int/standard_opt_out.csv") %>% 
  mutate(sos = as.factor(sos), info = as.factor(info), own = as.factor(own))


standard_clogit<-clogit(RES~ASC+sos+info+own+strata(STR), data=standard_opt_out)
standard_clogit
```

Pooled (Model II)
```{r}
pooled <- read_csv("int/pooled_data.csv")%>% 
  mutate(sos = as.factor(sos), info = as.factor(info), own = as.factor(own))


pooled_clogit<-clogit(RES~sos+info+own+strata(STR), data=pooled)
pooled_clogit
```

Unforced Responses (Model III)
```{r}
unforced <- read_csv("int/unforced_data.csv")%>% 
  mutate(sos = as.factor(sos), info = as.factor(info), own = as.factor(own))

unforced_clogit<-clogit(RES~sos+info+own+strata(STR), data=unforced)
unforced_clogit
```

Forced Responses (Model IV)
```{r}
forced <- read_csv("int/forced_data.csv")%>% 
  mutate(sos = as.factor(sos), info = as.factor(info), own = as.factor(own))

forced_clogit<-clogit(RES~sos+info+own+strata(STR), data=forced)
forced_clogit
```

```{r}
standard_clogit
pooled_clogit
unforced_clogit
forced_clogit
```

