---
title: "Analysis"
author: "*Compiled on `r date()` by `r Sys.info()['user']`*"
output: 
  html_document:
    toc: true
    toc_float: yes
    number_sections: true
    theme: cerulean
    highlight: haddock
    includes: 
  pdf_document:
    toc: true
editor_options: 
  chunk_output_type: console
---

## Summary
Mixed Logit Analysis on the DRCE conducted in Indonesia and Mexico. Split into four different models; Standard opt-out model (Model I), Pooled (Model II), Unforced Responses (Model III), and Forced Responses (Model IV).

## Data Source 
Personal Interviews
 
## Reference 
Panga Watch
 
## Downloaded
September 30, 2019
 
Time range: 
2019
 
## Format
comma separated values

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(survival)
library(AlgDesign)
library(DT)
library(stargazer)
library(xtable)
library(here)
library(kableExtra)

master_survey <- read.csv("raw/master_survey_resp.csv", stringsAsFactors = TRUE) %>%
  select(-start, -end, -survey_type, -interviewer, -comment, -text_vms_adoption, -fishery_problem_one, -fishery_problem_two, -fishery_problem_three, -fishery_solution_one, -fishery_solution_two, -fishery_solution_three, -photo)
```

## Standard opt-out model (Model I)
```{r}
standard_opt_out <- read_csv("int/standard_opt_out_fix.csv") %>%
  left_join(master_survey, by = "survey_id") %>%
  select(-noalt)
## Now we have ALL of the characteristics matched with each survey respondent and the correct data structure to plug into clogit. All you have to do is add whatever characteristic you want to the clogit function... i.e. age, years fishing, sex, village, etc... although I think you would have to add something like sos:country to determine the effect that country has on the sos attribute...

standard_clogit <- clogit(RES~ASC+sos+info+own.fisher+own.industry+own.gov + strata(survey_version), data=standard_opt_out) # run the clogit. ASC represents the alternative specific constant, or the opt out option.
summary(standard_clogit)

standard_clogit_char_test <- clogit(RES~ASC+sos+info+own.fisher+own.industry+own.gov + country + age + community + strata(STR), data=standard_opt_out)
standard_clogit_char_test

```

## Extrapolate predictions using standard clogit model
```{r}
standard_predictions <- predict(standard_clogit, newdata = standard_opt_out, type = "risk", se.fit = TRUE)

standard_predictions_data <- data.frame(standard_opt_out, standard_predictions) %>%
  select(STR, package, info, sos, own, RES, fit, se.fit)

#reasoning for predicting out a clogit model:
#https://markmail.org/search/?q=list%3Aorg.r-project.r-help+predict+clogit#query:list%3Aorg.r-project.r-help%20predict%20clogit%20from%3A%22Therneau%2C%20Terry%20M.%2C%20Ph.D.%22+page:1+mid:tsbl3cbnxywkafv6+state:results
#https://stackoverflow.com/questions/35329585/how-to-get-fitted-values-from-clogit-model

# sos	0 = no, 1 = yes
# info 	1= non, 0 = anon
# own	1 = fishers, 2 = industry, 3 = govt, 4 = public access
#adopt : 1 = accept, 0 = decline

standard_predictions_data_final <- standard_predictions_data %>%
  mutate(`probability (%)` = round(fit/(fit+ 1),4)*100,
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-`probability (%)`) %>%
  select(package, info, own, sos, `probability (%)`, level_se) %>%
  group_by(package, info, own, sos) %>%
  summarise(`probability (%)` = mean(`probability (%)`), level_se = mean(level_se))  %>%
  ungroup() %>%
  mutate(info = case_when(
    info == 0 ~ "Anon",
    info == 1 ~ "Non-Anon"
  ),
  own = case_when(
   own == 1 ~ "Fishers",
   own == 2 ~ "Industry",
   own == 3 ~ "Government",
   own == 4 ~ "Public Access"
  ),
  sos = case_when(
    sos == 0 ~ "No",
    sos == 1 ~ "Yes"
  )) %>%
  arrange(-`probability (%)`)



write.csv(standard_predictions_data_final, "output/standard_probs.csv", row.names = FALSE)

DT::datatable(standard_predictions_data)

## group by sos to get sos probability
standard_predictions_data_sos <- standard_predictions_data %>%
  mutate(`probability (%)` = round(fit/(fit+ 1),4)*100,
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-`probability (%)`) %>%
  select(package, info, own, sos, `probability (%)`, level_se) %>%
  group_by(sos) %>%
  summarise(`probability (%)` = mean(`probability (%)`), level_se = mean(level_se))

## group by info to get info probability
standard_predictions_data_info <- standard_predictions_data %>%
  mutate(`probability (%)` = round(fit/(fit+ 1),4)*100,
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-`probability (%)`) %>%
  select(package, info, own, sos, `probability (%)`, level_se) %>%
  group_by(info) %>%
  summarise(`probability (%)` = mean(`probability (%)`), level_se = mean(level_se))

## group by own to get own probability
standard_predictions_data_own <- standard_predictions_data %>%
  mutate(`probability (%)` = round(fit/(fit+ 1),4)*100,
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-`probability (%)`) %>%
  select(package, info, own, sos, `probability (%)`, level_se) %>%
  group_by(own) %>%
  summarise(`probability (%)` = mean(`probability (%)`), level_se = mean(level_se))
```



## Pooled (Model II)
```{r}
pooled <- read_csv("int/pooled_data_fix.csv") %>%
  left_join(master_survey, by = "survey_id") %>%
  select(-noalt) %>%
  mutate(own = as.factor(own))

pooled <- within(pooled, own <- relevel(own, ref = 1))

# pooled_clogit<-clogit(RES~sos+info+ own + strata(STR), data=pooled)
# summary(pooled_clogit)

pooled_clogit<-clogit(RES~sos+info+  own.fisher + own.industry  + own.gov + strata(STR), data=pooled)
summary(pooled_clogit)

```

```{r}
# make the graphs for actual preference weights

sos_coef <- pooled_clogit$coefficients[1]
info_coef <- pooled_clogit$coefficients[2]
own_1_coef <- pooled_clogit$coefficients[3]
own_2_coef <- pooled_clogit$coefficients[4]
own_3_coef <- pooled_clogit$coefficients[5]

pooled_clogit_coefs <- data.frame(names = names(pooled_clogit$coefficients), clogit_coef = pooled_clogit$coefficients)

avg_own <- (own_1_coef + own_2_coef + own_3_coef)/4
avg_info <- (info_coef)/2
avg_sos <- sos_coef/2

sos_actual <- pooled_clogit_coefs %>%
  filter(names == "sos") %>%
  mutate(actual = clogit_coef - avg_sos)

sos0_actual <- data.frame(names = "sos0", 0, actual = -sum(sos_actual$actual)) %>%
  rename("clogit_coef" = "X0")

sos_actual_final <- rbind(sos_actual, sos0_actual)

sos_actual_final <- rbind(sos_actual, sos0_actual)

info_actual <- pooled_clogit_coefs %>%
  filter(names == "info") %>%
  mutate(actual = clogit_coef - avg_info)

info0_actual <- data.frame(names = "info0", 0, actual = -sum(info_actual$actual)) %>%
  rename("clogit_coef" = "X0")

info_actual_final <- rbind(info_actual, info0_actual)

own_actual <- pooled_clogit_coefs %>%
  filter(str_detect(names, 'own') ) %>%
  mutate(actual = clogit_coef - avg_own)

own4_actual <- data.frame(names = "own.public",  0, actual =-sum(own_actual$actual)) %>%
  rename("clogit_coef" = "X0")

own_actual_final <- rbind(own_actual, own4_actual)

all_actual <- rbind(sos_actual_final, info_actual_final, own_actual_final) %>% 
  select(-clogit_coef)
write.csv(all_actual, "output/pooled_clogit_actual_coefs.csv", row.names = FALSE)

all_actual <- read_csv("output/pooled_clogit_actual_coefs.csv")

positions <- c("sos", "sos0", "info", "info0", "own.fisher", "own.industry", "own.gov", "own.public")

all_actual %>%
  ggplot(aes(x= names, y= actual)) +
  geom_col() + 
  theme_bw() +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(breaks = seq(-1.3, 1.3, 0.1)) %>%
  labs(y = "Preference Weights")

# own_4 <-sos_coef*1 + info_coef*1
# 
# own_1_new <- own_4 + own_1_coef
# own_2_new <- own_4 + own_2_coef
# own_3_new <- own_4 + own_3_coef
# sos_new <- sos_coef + own_4
# info_new <- info_coef + own_4
```

Unforced Responses (Model III)
```{r}
unforced <- read_csv("int/unforced_data_fix.csv") %>%
  left_join(master_survey, by = "survey_id") %>%
  select(-noalt)

unforced_clogit<-clogit(RES~sos+info+own.fisher+own.industry+own.gov+strata(STR), data=unforced)
unforced_clogit
```

Forced Responses (Model IV)
```{r}
forced <- read_csv("int/forced_data_fix.csv") %>%
  left_join(master_survey, by = "survey_id") %>%
  select(-noalt)

forced_clogit<-clogit(RES~sos+info+own.fisher+own.industry+own.gov+own.public+strata(STR), data=forced)
forced_clogit
```


**Likelihood Ratio Test Taken from Penn et al.**
```{r}
#K = 5
#M = 2

pooled_log <- logLik(pooled_clogit) #-74.11078 (df=5)
unforced_log <- logLik(unforced_clogit) #-42.90397 (df=5)
forced_log <- logLik(forced_clogit) #-22.24721 (df=5)

-2*(logLik(pooled_clogit) - (logLik(unforced_clogit) + logLik(forced_clogit)))
-2*(pooled_log- (unforced_log + forced_log))

-2*(74.11078 - (42.90397 + 22.24721)) #17.9192
# if this then 17.9192 < 20.52 which means that we do not reject the null that there is no difference between the forced and unforced........... need to write this up formally

```

Methods Log Lik Test:
We can test the effect of forced choice versus unforced choice using a likelihood ratio test for equality. The test statistic is:

$$ -2*(LL_{r} - \sum LL{u}) $$
Which is chi-squared distributed with K(M-1) degrees of freedom, where K is the number of restrictions (5), M is the number of treatments (2). The null hypothesis of the test is that the parameters are not significantly different between treatments. This means that if we do not reject the null, we can use the standard opt out method without worry of respondent bias. If the test statistic exceeds the critical value, found in the chi square table, then evidence suggests that the treatments sufficiently contribute to explaining the model and reject the null hypothesis of no difference between the forced and unforced datasets. 



**Make pooled predictions using linear predictors given from model and calculate marginal probabilities based off of the status quo and GFW tech**
```{r}
fitted_pooled <- data.frame(lin_pred = pooled_clogit$linear.predictors) 

new_pooled <- pooled %>%
  select(package, STR, info, sos, own)

model_preds_pooled <- cbind(new_pooled, fitted_pooled) %>% 
  mutate(probs = exp(lin_pred)/(1 + exp(lin_pred)))

preds_pooled <- model_preds_pooled %>%
  group_by(package, info, sos, own) %>%
  summarise(probs = mean(probs))

write.csv(preds_pooled, "output/pooled_probs.csv", row.names = FALSE)

# the status quo probability; Anonymous (info = 0), No SOS (sos = 0), Owned by fishermen (own = 1)
status_quo <- preds_pooled$probs[preds_pooled$package == 15]
#0.3826569

## Make status quo non-anonymous; Non-Anonymous (info = 1), No SOS (sos = 0), Owned by fishermen (own = 1)
add_non_anon <- preds_pooled$probs[preds_pooled$package == 3]
#0.3520571

## Make status quo with SOS; Anonymous (info = 0), SOS (sos = 1), Owned by fishermen (own = 1)
add_sos <- preds_pooled$probs[preds_pooled$package == 7]

## Make status quo own by ind; Anonymous (info = 0), no SOS (sos = 0), Owned by industry (own = 2)
add_own_by_ind <- preds_pooled$probs[preds_pooled$package == 10]

## Make status quo own by gov; Anonymous (info = 0), no SOS (sos = 0), Owned by government (own = 3)
add_own_by_gov <- preds_pooled$probs[preds_pooled$package == 6]

## Make status quo own by public; Anonymous (info = 0), no SOS (sos = 0), Owned by public (own = 4)
add_own_by_public <- preds_pooled$probs[preds_pooled$package == 5]

### Adding non anon to status quo results in a 3.06% decrease
lin_pred_add_non_anon <-  status_quo - add_non_anon

### adding sos to status quo results in a 49.56586% increase
lin_pred_add_sos <- status_quo - add_sos

### adding industry ownership results in a 26.30367% decrease
lin_pred_add_ind <- status_quo - add_own_by_ind

### adding government ownership results in a 0.5339% increase
lin_pred_add_gov <- status_quo - add_own_by_gov

### adding public access results in a 22.59136% decrease
lin_pred_add_public <- status_quo - add_own_by_public

# the status quo GFW probability; Non-Anonymous (info = 1), SOS (sos = 1), Public access (own = 4)
GFW_prob <- preds_pooled$probs[preds_pooled$package == 11]
#0.65486

# GFW probabilty with anonymous; Anonymous (info = 0), SOS (sos = 1), Public (own = 4)
add_anon_GFW <- preds_pooled$probs[preds_pooled$package == 4]

# GFW probabilty with no SOS; non Anonymous (info = 1), no SOS (sos = 0), Public (own = 4)
add_no_sos_GFW <- preds_pooled$probs[preds_pooled$package == 8]

# GFW probabilty owned by gov; non Anonymous (info = 1), SOS (sos = 1), government (own = 3)
add_gov_GFW <- preds_pooled$probs[preds_pooled$package == 2]

# GFW probabilty owned by ind; non Anonymous (info = 1), SOS (sos = 1), industry (own = 2)
add_ind_GFW <- preds_pooled$probs[preds_pooled$package == 13]

# GFW probabilty owned by fish; non Anonymous (info = 1), SOS (sos = 1), fisher (own = 1)
add_fisher_GFW <- preds_pooled$probs[preds_pooled$package == 12]

### Adding anon to GFW status quo results in a 2.913529% increase
lin_pred_GFW_add_anon <- GFW_prob - add_anon_GFW

### adding no sos to GFW status quo results in a 51.47519% decrease
lin_pred_GFW_add_no_sos <- GFW_prob- add_no_sos_GFW

### adding government ownership to GFW status quo results in a 21.12957% increase
lin_pred_GFW_add_gov <-  GFW_prob - add_gov_GFW

### adding industry ownership to GFW status quo results in a 7.380583% decrease
lin_pred_GFW_add_ind <- GFW_prob - add_ind_GFW

### adding fisher ownership to GFW status quo results in a 20.86605% increase
lin_pred_GFW_add_fisher <- GFW_prob - add_fisher_GFW
```

**Make pooled predictions using predict() and calculate marginal probabilities based off of the status quo and GFW tech**

```{r}
#predictions for pooled data

library(AlgDesign)
ffd <- gen.factorial(c(2,2,4), varNames = c("sos", "info", "own"), factors = "all") # construct a full factorial design which has two 2 level attributes and one 4 level attribute. factors = "all" indicates that all arguments are factors
ffd 

all_packages <- ffd %>%
  mutate(STR = 1001) %>% 
  mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,0,1)) %>%
  mutate(own.fisher=ifelse(own==1,1,0), own.industry=ifelse(own==2,1,0), own.gov=ifelse(own==3,1,0), own.public=ifelse(own==4,1,0)) 

#pooled_predictions <- predict(pooled_clogit, newdata = pooled, type = "expected", se.fit = TRUE) #this gives relative probs within strata. 

pooled_predictions <- predict(pooled_clogit, newdata = all_packages, type = "risk", se.fit = TRUE) #this gives absolute probabilities? 


pooled_predictions_data <- data.frame(all_packages, pooled_predictions) #%>%
  #select(STR, package, info, sos, own, RES, fit)

#reasoning for predicting out a clogit model:
#https://markmail.org/search/?q=list%3Aorg.r-project.r-help+predict+clogit#query:list%3Aorg.r-project.r-help%20predict%20clogit%20from%3A%22Therneau%2C%20Terry%20M.%2C%20Ph.D.%22+page:1+mid:tsbl3cbnxywkafv6+state:results
#https://stackoverflow.com/questions/35329585/how-to-get-fitted-values-from-clogit-model

# sos	0 = no, 1 = yes
# info 	1 = non, 0 = anon
# own	1 = fishers, 2 = industry, 3 = govt, 4 = public access
#adopt : 1 = accept, 0 = decline

pooled_predictions_data <- pooled_predictions_data %>%
  mutate(level_probs1 = fit/(fit+ 1),
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-level_probs1) %>%
  select(info, own, sos, own.fisher, own.industry, own.gov, own.public, level_probs1, level_se) 
# %>%
#   mutate(info = case_when(
#     info == 0 ~ "Anon",
#     info == 1 ~ "Non-Anon"
#   ),
#   own = case_when(
#    own == 1 ~ "Fishers",
#    own == 2 ~ "Industry",
#    own == 3 ~ "Government",
#    own == 4 ~ "Public Access"
#   ),
#   sos = case_when(
#     sos == 0 ~ "No",
#     sos == 1 ~ "Yes"
#   ))

# the status quo probability; Anonymous (info = 0), No SOS (sos = 0), Owned by fishermen (own = 1)
status_quo_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 0 & pooled_predictions_data$sos == 0 & pooled_predictions_data$own == 1 ]
#0.3636907

## Make status quo non-anonymous; Non-Anonymous (info = 1), No SOS (sos = 0), Owned by fishermen (own = 1)
add_non_anon_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 1 & pooled_predictions_data$sos == 0 & pooled_predictions_data$own == 1 ]
#0.33337876

## Make status quo with SOS; Anonymous (info = 0), SOS (sos = 1), Owned by fishermen (own = 1)
add_sos_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 0 & pooled_predictions_data$sos == 1 & pooled_predictions_data$own == 1 ]
#0.869379027

## Make status quo own by ind; Anonymous (info = 0), no SOS (sos = 0), Owned by industry (own = 2)
add_own_by_ind_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 0 & pooled_predictions_data$sos == 0 & pooled_predictions_data$own == 2 ]

## Make status quo own by gov; Anonymous (info = 0), no SOS (sos = 0), Owned by government (own = 3)
add_own_by_gov_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 0 & pooled_predictions_data$sos == 0 & pooled_predictions_data$own == 3 ]

## Make status quo own by public; Anonymous (info = 0), no SOS (sos = 0), Owned by public (own = 4)
add_own_by_public_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 0 & pooled_predictions_data$sos == 0 & pooled_predictions_data$own == 4 ]

### Adding non anon to status quo results in a 2.99% decrease
predict_add_non_anon <- status_quo_predict - add_non_anon_predict

### adding sos to status quo results in a 50.56883% increase
predict_add_sos <- status_quo_predict - add_sos_predict

### adding industry ownership results in a 25.23507% decrease
predict_add_ind <- status_quo_predict - add_own_by_ind_predict

### adding government ownership results in a 0.5233067% increase
predict_add_gov <- status_quo_predict - add_own_by_gov_predict

### adding public access results in a 21.73703% decrease
predict_add_public <- status_quo_predict - add_own_by_public_predict


# the status quo GFW probability; Non-Anonymous (info = 1), SOS (sos = 1), Public access (own = 4)
GFW_prob_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 1 & pooled_predictions_data$sos == 1 & pooled_predictions_data$own == 4 ]
#0.65486

# GFW probabilty with anonymous; Anonymous (info = 0), SOS (sos = 1), Public (own = 4)
add_anon_GFW_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 0 & pooled_predictions_data$sos == 1 & pooled_predictions_data$own == 4 ]

# GFW probabilty with no SOS; non Anonymous (info = 1), no SOS (sos = 0), Public (own = 4)
add_no_sos_GFW_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 1 & pooled_predictions_data$sos == 0 & pooled_predictions_data$own == 4 ]

# GFW probabilty owned by gov; non Anonymous (info = 1), SOS (sos = 1), government (own = 3)
add_gov_GFW_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 1 & pooled_predictions_data$sos == 1 & pooled_predictions_data$own == 3 ]

# GFW probabilty owned by ind; non Anonymous (info = 1), SOS (sos = 1), industry (own = 2)
add_ind_GFW_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 1 & pooled_predictions_data$sos == 1 & pooled_predictions_data$own == 2 ]

# GFW probabilty owned by fish; non Anonymous (info = 1), SOS (sos = 1), fisher (own = 1)
add_fisher_GFW_predict <- pooled_predictions_data$level_probs1[pooled_predictions_data$info == 1 & pooled_predictions_data$sos == 1 & pooled_predictions_data$own == 1 ]

### Adding anon to GFW status quo results in a 2.990312% increase
predict_GFW_add_anon <- GFW_prob_predict - add_anon_GFW_predict

### adding no sos to GFW status quo results in a 50.56883% decrease
predict_GFW_add_no_sos <- GFW_prob_predict - add_no_sos_GFW_predict

### adding government ownership to GFW status quo results in a 22.01639% increase
predict_GFW_add_gov <- GFW_prob_predict - add_gov_GFW_predict

### adding industry ownership to GFW status quo results in a 7.51147% decrease
predict_GFW_add_ind <- GFW_prob_predict - add_ind_GFW_predict

### adding fisher ownership to GFW status quo results in a 21.73703% increase
predict_GFW_add_fisher <- GFW_prob_predict - add_fisher_GFW_predict

```

**Make pooled predictions using what we think to be the output formula for logistic regression and calculate marginal probabilities based off of the status quo and GFW tech**
```{r}
### Calculate probabiltiies using formula ###

#make function from pooled model output
clogit_pooled_fxn <- function(info, sos, own.fisher, own.industry, own.gov){
  prob <- exp(info_coef*info + sos_coef*sos + own_1_coef*own.fisher + own_2_coef*own.industry + own_3_coef*own.gov)/(1+ exp(info_coef*info + sos_coef*sos + own_1_coef*own.fisher + own_2_coef*own.industry + own_3_coef*own.gov))
  
  return(prob)
}

pooled_predictions_data_form <- pooled_predictions_data %>%
  select(-level_probs1, -level_se) %>%
  mutate(info = as.integer(info), sos = as.integer(sos), own.fisher = as.integer(own.fisher), own.industry = as.integer(own.industry), own.gov = as.integer(own.gov)) %>%
  select(info, sos, own, own.fisher, own.industry, own.gov, own.public)


preds_pooled_form <- cbind(pooled_predictions_data_form, data.frame(probs = clogit_pooled_fxn(pooled_predictions_data_form$info, pooled_predictions_data_form$sos, pooled_predictions_data_form$own.fisher, pooled_predictions_data_form$own.industry, pooled_predictions_data_form$own.gov)))

# the status quo probability using formula; Anonymous (info = 0), No SOS (sos = 0), Owned by fishermen (own = 1)
status_quo_form <- preds_pooled_form$probs[preds_pooled_form$info == 0 & preds_pooled_form$sos == 0 & preds_pooled_form$own == 1]
#0.7693022

## Make status quo non-anonymous; Non-Anonymous (info = 1), No SOS (sos = 0), Owned by fishermen (own = 1)
add_non_anon_form <- preds_pooled_form$probs[preds_pooled_form$info == 1 & preds_pooled_form$sos == 0 & preds_pooled_form$own == 1]
#0.7451011

## Make status quo with SOS; Anonymous (info = 0), SOS (sos = 1), Owned by fishermen (own = 1)
add_sos_form <- preds_pooled_form$probs[preds_pooled_form$info == 0 & preds_pooled_form$sos == 1 & preds_pooled_form$own == 1]
#0.974894

## Make status quo own by ind; Anonymous (info = 0), SOS (sos = 0), Owned by industry (own = 2)
add_own_by_ind_form <- preds_pooled_form$probs[preds_pooled_form$info == 0 & preds_pooled_form$sos == 0 & preds_pooled_form$own == 2]

## Make status quo own by gov; Anonymous (info = 0), SOS (sos = 0), Owned by government (own = 3)
add_own_by_gov_form <- preds_pooled_form$probs[preds_pooled_form$info == 0 & preds_pooled_form$sos == 0 & preds_pooled_form$own == 3]

## Make status quo own by public; Anonymous (info = 0), SOS (sos = 0), Owned by public (own = 4)
add_own_by_public_form <- preds_pooled_form$probs[preds_pooled_form$info == 0 & preds_pooled_form$sos == 0 & preds_pooled_form$own == 4]

### Adding non anon to status quo results in a 2.420118% decrease
form_add_non_anon <- status_quo_form - add_non_anon_form

### adding sos to status quo results in a 20.55921% increase
form_add_sos <- status_quo_form - add_sos_form

### adding industry ownership results in a 34.70097% decrease
form_add_ind <- status_quo_form - add_own_by_ind_form

### adding government ownership results in a .3976774% increase
form_add_gov <- status_quo_form - add_own_by_gov_form

### adding public access results in a 26.93023% decrease
form_add_public <- status_quo_form - add_own_by_public_form




# the status quo GFW probability; Non-Anonymous (info = 1), SOS (sos = 1), Public access (own = 4)
GFW_prob_form <- preds_pooled_form$probs[preds_pooled_form$info == 1 & preds_pooled_form$sos == 1 & preds_pooled_form$own == 4]
#0.65486

# GFW probabilty with anonymous; Anonymous (info = 0), SOS (sos = 1), Public (own = 4)
add_anon_GFW_form <- preds_pooled_form$probs[preds_pooled_form$info == 0 & preds_pooled_form$sos == 1 & preds_pooled_form$own == 4]

# GFW probabilty with no SOS; non Anonymous (info = 1), no SOS (sos = 0), Public (own = 4)
add_no_sos_GFW_form <- preds_pooled_form$probs[preds_pooled_form$info == 1 & preds_pooled_form$sos == 0 & preds_pooled_form$own == 4]

# GFW probabilty owned by gov; non Anonymous (info = 1), SOS (sos = 1), government (own = 3)
add_gov_GFW_form <- preds_pooled_form$probs[preds_pooled_form$info == 1 & preds_pooled_form$sos == 1 & preds_pooled_form$own == 3]

# GFW probabilty owned by ind; non Anonymous (info = 1), SOS (sos = 1), industry (own = 2)
add_ind_GFW_form <- preds_pooled_form$probs[preds_pooled_form$info == 1 & preds_pooled_form$sos == 1 & preds_pooled_form$own == 2]

# GFW probabilty owned by fish; non Anonymous (info = 1), SOS (sos = 1), fishermen (own = 1)
add_fisher_GFW_form <- preds_pooled_form$probs[preds_pooled_form$info == 1 & preds_pooled_form$sos == 1 & preds_pooled_form$own == 1]

### Adding anon to GFW status quo results in a 1.014091% increase
form_GFW_add_anon <- GFW_prob_form - add_anon_GFW_form

### adding no sos to GFW status quo results in a 44.36584% decrease
form_GFW_add_no_sos <- GFW_prob_form - add_no_sos_GFW_form

### adding government ownership to GFW status quo results in a 6.130375% increase
form_GFW_add_gov <- GFW_prob_form - add_gov_GFW_form

### adding industry ownership to GFW status quo results in a 2.895636% decrease
form_GFW_add_ind <- GFW_prob_form - add_ind_GFW_form

### adding fisher ownership to GFW status quo results in a 6.068531% increase
form_GFW_add_fisher <- GFW_prob_form - add_fisher_GFW_form


comp_lin_pred <- -1*100*data.frame(lin_pred_add_non_anon, lin_pred_add_sos, lin_pred_add_ind, lin_pred_add_gov, lin_pred_add_public) %>%
  rename( "add_non_anon" = 1, "add_sos" = 2, "add_ind" = 3, "add_gov" = 4, "add_public" = 5) 
rownames(comp_lin_pred) <- "lin_pred"

comp_predict <- -1*100*data.frame(predict_add_non_anon, predict_add_sos, predict_add_ind, predict_add_gov, predict_add_public) %>%
  rename( "add_non_anon" = 1, "add_sos" = 2, "add_ind" = 3, "add_gov" = 4, "add_public" = 5)
rownames(comp_predict) <- "predict"

comp_formula <- -1*100*data.frame(form_add_non_anon, form_add_sos, form_add_ind, form_add_gov, form_add_public) %>%
  rename( "add_non_anon" = 1, "add_sos" = 2, "add_ind" = 3, "add_gov" = 4, "add_public" = 5)
rownames(comp_formula) <- "formula"

comp_lin_pred_gfw <- -1*100*data.frame(lin_pred_GFW_add_anon, lin_pred_GFW_add_no_sos, lin_pred_GFW_add_anon, lin_pred_GFW_add_ind, lin_pred_GFW_add_gov) %>%
  rename( "gfw_add_anon" = 1, "gfw_add_no_sos" = 2, "gfw_add_fisher" = 3, "gfw_add_ind" = 4, "gfw_add_gov" = 5) 
rownames(comp_lin_pred_gfw) <- "lin_pred"

comp_predict_gfw <- -1*100*data.frame(predict_GFW_add_anon, predict_GFW_add_no_sos, predict_GFW_add_anon, predict_GFW_add_ind, predict_GFW_add_gov) %>%
  rename( "gfw_add_anon" = 1, "gfw_add_no_sos" = 2, "gfw_add_fisher" = 3, "gfw_add_ind" = 4, "gfw_add_gov" = 5) 
rownames(comp_predict_gfw) <- "predict"

comp_formula_gfw <- -1*100*data.frame(form_GFW_add_anon, form_GFW_add_no_sos, form_GFW_add_anon, form_GFW_add_ind, form_GFW_add_gov) %>%
  rename( "gfw_add_anon" = 1, "gfw_add_no_sos" = 2, "gfw_add_fisher" = 3, "gfw_add_ind" = 4, "gfw_add_gov" = 5) 
rownames(comp_formula_gfw) <- "formula"

final_reg <- rbind(comp_lin_pred, comp_predict, comp_formula)

final_gfw <- rbind(comp_lin_pred_gfw, comp_predict_gfw, comp_formula_gfw)

final_combined_clogit_marg_probs <- cbind(final_reg, final_gfw)

write.csv(final_combined_clogit_marg_probs, "output/unformatted_clogit_marg_probs.csv", row.names = TRUE)

## combine all forms of calculating probs
newnew <- left_join(preds_pooled, preds_pooled_form, by = c("info", "sos", "own"))

newnewnew <- left_join(newnew, pooled_predictions_data, by = c("info", "sos", "own")) %>%
  select(package, info, sos, own, lin_pred_probs = probs.x, probs_form = probs.y, predict_probs = level_probs1 )

write.csv(newnewnew, "output/clogit_pooled_probs.csv", row.names = FALSE)
```

**Make forced predictions data using predict()**
```{r}
#forced predictions 

forced_predictions <- predict(forced_clogit, newdata = all_packages, type = "risk", se.fit = TRUE)

forced_predictions_data <- data.frame(all_packages, forced_predictions)  

#reasoning for predicting out a clogit model:
#https://markmail.org/search/?q=list%3Aorg.r-project.r-help+predict+clogit#query:list%3Aorg.r-project.r-help%20predict%20clogit%20from%3A%22Therneau%2C%20Terry%20M.%2C%20Ph.D.%22+page:1+mid:tsbl3cbnxywkafv6+state:results
#https://stackoverflow.com/questions/35329585/how-to-get-fitted-values-from-clogit-model

# sos	0 = no, 1 = yes
# info 	1 = non, 0 = anon
# own	1 = fishers, 2 = industry, 3 = govt, 4 = public access
#adopt : 1 = accept, 0 = decline

forced_predictions_data <- forced_predictions_data %>%
  mutate(level_probs1 = fit/(fit+ 1),
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-level_probs1) %>%
  select(info, own, sos, level_probs1, level_se) %>%
  mutate(info = case_when(
    info == 0 ~ "Anon",
    info == 1 ~ "Non-Anon"
  ), 
  own = case_when(
   own == 1 ~ "Fishers",
   own == 2 ~ "Industry", 
   own == 3 ~ "Government", 
   own == 4 ~ "Public Access"
  ),
  sos = case_when(
    sos == 0 ~ "No",
    sos == 1 ~ "Yes"
  ))

write.csv(forced_predictions_data, "output/forced_probs.csv", row.names = FALSE)

DT::datatable(forced_predictions_data)
```

**Make unforced prediction using predict()**
```{r}
#unforced predictions 

unforced_predictions <- predict(unforced_clogit, newdata = all_packages, type = "risk", se.fit = TRUE)

unforced_predictions_data <- data.frame(all_packages, unforced_predictions)  

#reasoning for predicting out a clogit model:
#https://markmail.org/search/?q=list%3Aorg.r-project.r-help+predict+clogit#query:list%3Aorg.r-project.r-help%20predict%20clogit%20from%3A%22Therneau%2C%20Terry%20M.%2C%20Ph.D.%22+page:1+mid:tsbl3cbnxywkafv6+state:results
#https://stackoverflow.com/questions/35329585/how-to-get-fitted-values-from-clogit-model

# sos	0 = no, 1 = yes
# info 	1 = non, 0 = anon
# own	1 = fishers, 2 = industry, 3 = govt, 4 = public access
#adopt : 1 = accept, 0 = decline

unforced_predictions_data <- unforced_predictions_data %>%
  mutate(level_probs1 = fit/(fit+ 1),
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-level_probs1) %>%
  select(info, own, sos, level_probs1, level_se) %>%
  mutate(info = case_when(
    info == 0 ~ "Anon",
    info == 1 ~ "Non-Anon"
  ), 
  own = case_when(
   own == 1 ~ "Fishers",
   own == 2 ~ "Industry", 
   own == 3 ~ "Government", 
   own == 4 ~ "Public Access"
  ),
  sos = case_when(
    sos == 0 ~ "No",
    sos == 1 ~ "Yes"
  ))

write.csv(unforced_predictions_data, "output/unforced_probs.csv", row.names = FALSE)

DT::datatable(unforced_predictions_data)
#0.9881482 

p = (exp(unforced_clogit$coefficients[1]*1 + unforced_clogit$coefficients[2]*1 + unforced_clogit$coefficients[3]*1 + unforced_clogit$coefficients[4]*0 + unforced_clogit$coefficients[5]*0))/(1 + exp( unforced_clogit$coefficients[1]*1+ unforced_clogit$coefficients[2]*1 + unforced_clogit$coefficients[3]*1 + unforced_clogit$coefficients[4]*0+ unforced_clogit$coefficients[5]*0))
p     
#0.9881482 

```

**Make standard predictions using predict()**
```{r}
#standard predictions
all_packages_standard <- all_packages %>%
  mutate(ASC = 1) 


standard_predictions <- predict(standard_clogit, newdata = standard_opt_out, type = "risk", se.fit = TRUE)

standard_predictions_data <- data.frame(standard_opt_out, standard_predictions) %>%
  select(STR, package, info, sos, own, RES, fit, se.fit)

#reasoning for predicting out a clogit model:
#https://markmail.org/search/?q=list%3Aorg.r-project.r-help+predict+clogit#query:list%3Aorg.r-project.r-help%20predict%20clogit%20from%3A%22Therneau%2C%20Terry%20M.%2C%20Ph.D.%22+page:1+mid:tsbl3cbnxywkafv6+state:results
#https://stackoverflow.com/questions/35329585/how-to-get-fitted-values-from-clogit-model

# sos	0 = no, 1 = yes
# info 	1= non, 0 = anon
# own	1 = fishers, 2 = industry, 3 = govt, 4 = public access
#adopt : 1 = accept, 0 = decline

standard_predictions_data <- standard_predictions_data %>%
  mutate(`probability (%)` = round(fit/(fit+ 1),4)*100,
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-`probability (%)`) %>%
  select(package, info, own, sos, `probability (%)`, level_se) %>%
  group_by(package, info, own, sos) %>%
  summarise(`probability (%)` = mean(`probability (%)`), level_se = mean(level_se)) 
  # mutate(info = case_when(
  #   info == 0 ~ "Anon",
  #   info == 1 ~ "Non-Anon"
  # ), 
  # own = case_when(
  #  own == 1 ~ "Fishers",
  #  own == 2 ~ "Industry", 
  #  own == 3 ~ "Government", 
  #  own == 4 ~ "Public Access"
  # ),
  # sos = case_when(
  #   sos == 0 ~ "No",
  #   sos == 1 ~ "Yes"
  # ))

write.csv(standard_predictions_data, "output/standard_probs.csv", row.names = FALSE)

DT::datatable(standard_predictions_data)
```


# BLR including WTP
```{r}
#data formatting 
choice<- read.csv("raw/version_to_package.csv", stringsAsFactors = TRUE) %>% 
  rename(survey_version = 1)

packages<- read.csv("raw/packages.csv", stringsAsFactors = TRUE)  %>% 
  rename(package = 1)

choice_package<-choice %>% 
  left_join(packages) %>% 
  mutate(choice = ifelse(package <=16,1,2))

survey <- read_csv("raw/master_survey_resp.csv")

 





pack_no <- survey %>% 
  filter(package_nopackage == 0) %>% 
  mutate(wtp = ifelse(wtr_4== "y", -4,
                      ifelse(wtr_4== "n", -5,
                             ifelse(wtr_3=="y", -3,
                                    ifelse(wtr_2=="y", -2, -1))))) %>% 
  select(-starts_with("wtp_"), -starts_with("wtr_"), -package_nopackage) %>% 
  left_join(choice_package) %>% 
  mutate(choice=1)

pack_no_no<-pack_no %>% 
  mutate(wtp=(wtp+1)) %>% 
  mutate(choice = 0)

pack_yes_no<-pack_yes %>% 
  filter(wtp!=4) %>% 
  mutate(wtp=(wtp+1)) %>% 
  mutate(choice = 0)

bind_pre<-rbind(pack_no,pack_yes, pack_no_no, pack_yes_no) %>% 
  filter(wtp!=-5)

other_pack<-bind_pre %>% 
  select(survey_id, survey_version, country,  choice) %>%
  mutate(choice = ifelse(choice == 1,2,1)) %>% 
  left_join(choice_package) %>% 
  mutate(choice=0) %>% 
  mutate(wtp=0)

bind<-rbind(bind_pre, other_pack)  
```

For IND

wtp_1 = $2.14
wtp_2 = $3.56
wtp_3 = $5.35
wtp_4 = $7.12

For MEX 

wtp_1 = $2.07
wtp_2 = $3.62
wtp_3 = $5.17
wtp_4 = $7.75

```{r}
wtp_USD<-data.frame("level"=0:4,  "USD" = c(0,2.07, 3.56, 5.17, 7.12))

wtr_USD<-data.frame("level"=-1:-4,  "USD" = c(-2.07, -3.56, -5.17, -7.12))

USD<-rbind(wtp_USD, wtr_USD)

usd1<-USD %>% 
  mutate(bid1=level)

usd2<-USD %>% 
  mutate(bid2=level)

library(DCchoice)
ahelp(DCchoice)

survey <- read_csv("raw/master_survey_resp.csv") 

pack_yes<- survey %>% 
  select(survey_id, starts_with("wtp_"), starts_with("wtr_")) %>% 
  mutate(wtp = ifelse(wtp_1 == "n", 0,
                      ifelse(wtp_2 == "n", 1,
                             ifelse(wtp_3 == "n", 2,
                                    ifelse(wtp_4 == "n", 3, 
                                           ifelse(wtp_4 == "y", 4, "NA")))))) %>% 
  mutate(wtr = ifelse(wtr_1== "y", -1,
                      ifelse(wtr_2== "y", -2,
                             ifelse(wtr_3=="y", -3,
                                    ifelse(wtr_4=="y", -4, -5)))))

yn<-pack_yes %>% 
  filter(wtp!=4) %>% 
  select(survey_id, wtp) %>%
  mutate(wtp=as.integer(wtp)) %>% 
  mutate(R1=1, R2=0, bid1=wtp, bid2=wtp+1) %>% 
  select(-wtp)

yy<-pack_yes %>% 
  filter(wtp==4) %>% 
  select(survey_id, wtp) %>%
  mutate(wtp=as.integer(wtp)) %>% 
  mutate(R1=1, R2=1, bid1=wtp-1, bid2=wtp) %>% 
  select(-wtp)

ny<-pack_yes %>% 
  filter(wtr!=-5) %>% 
  select(survey_id, wtr) %>%
  mutate(wtr=as.integer(wtr)) %>% 
  mutate(R1=0, R2=1, bid1=wtr+1, bid2=wtr) %>% 
  select(-wtr)

nn<-pack_yes %>% 
  filter(wtr==-5) %>% 
  select(survey_id, wtr) %>%
  mutate(wtr=as.integer(wtr)) %>% 
  mutate(R1=0, R2=0, bid1=wtr+2, bid2=wtr+1) %>% 
  select(-wtr)

dchoice<-bind_rows(yn, yy, ny, nn)

dc_usd<-dchoice %>% 
  left_join(usd1, by="bid1") %>% 
  left_join(usd2, by="bid2") %>% 
  mutate(bid1=USD.x, bid2=USD.y) %>% 
  select(survey_id, bid1, bid2, R1, R2)

dc_package<-survey %>% 
  select(survey_id, survey_version, choice) %>% 
  left_join(choice_package) %>% 
  right_join(dc_usd) %>% 
  select(-survey_version, -choice, -package) %>% 
  mutate(sos=sos-1) %>% 
  mutate(info=-(info-2)) %>% 
  mutate(own=as.factor(own))

fmdb <- R1 + R2 ~ sos + info + own | bid1+bid2

NPdb <- dbchoice(fmdb, data = dc_package, dist = "logistic")

summary(NPdb)


# The Bootstrap method
set.seed(123) 
bootCI(NPdb)

# DBDC model
plot(NPdb, las = 1, xlab = "Bid amounts in USD", main = "DBDC model", cex.main = 0.8, 
    font.main = 4, xlim = c(-10, 10))
```

```{r}
install.packages("DCchoice",
repos = c("@CRAN@", "http://www.bioconductor.org/packages/release/bioc"),
dep = TRUE)

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("Icens")
```

