---
title: "Demographic Distribution"
author: "BR"
date: "28/11/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(DT)
library(kableExtra)
library(ggplot2)
```


```{r, include=FALSE}
# Read in all of the raw data
survey <- read_csv("raw/master_survey_resp.csv")
```
Question label 
Purpose of Survey
Survey ID
Survey Version
Name of Interviewer
Affiliated Organization
1. Country
2. Community Name
3. Gender of Interviewed


### 4. Fishing Gear Used 
In the last 12 months, what fishing gear have you used?
```{r, echo=FALSE}
q4<-survey %>% 
  mutate(gear_buceo = ifelse(grepl("Buceo", other_gear), 1, 0)) %>% 
  select(starts_with("gear")) %>% 
  na.omit() 


oldnames4<-colnames(q4)
newnames4 <- c("Hand Line", "Spear", "Traps", "Stationary Net",  "Mobile Net", "Stationary Line", "Other", "*Buceo")

q4_response<-survey %>% 
  select(starts_with("gear")) %>% 
  na.omit() %>% 
  nrow()

q4_sum<-q4 %>% 
  rename_at(vars(oldnames4), ~ newnames4)%>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(gear, Count) %>% 
  mutate(Percent = round((Count/q4_response)*100, 0)) %>% 
  rename(Gear = 1)
```
**Total Responses** = `r q4_response`

```{r, echo=FALSE}
q4_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other
```{r}
#Other Gear Indicated 
```

### 5. Status of Boat Ownership 
For fishing purposes, do you own a boat, share a boat, or rent a boat from others, or do not use a boat?
```{r, echo=FALSE}
q5_response<-survey %>% 
  select(starts_with("boat_status")) %>% 
  na.omit() %>% 
  nrow()


q5_sum<-survey %>% 
  select(starts_with("boat_status")) %>%
  mutate(boat_status= recode(boat_status,
                             "own"=	"Own",
                             "share_employee"=	"Share with others as part of a collective",
                             "share_collective"=	"Share with others as an employee",
                             "rent"=	"Rent from others",
                             "none"=	"Do not use a boat to fish")) %>% 
  group_by(boat_status) %>% 
  count() %>%
  rename("status"=1, "Count"=2)
```

```{r, echo=FALSE}
q5_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 6. Vessel Characteristics
For your primary fishing vessel, please describe the boat in the following aspects:

#### a. Length
```{r, echo=FALSE}
q6a_response<-survey %>% 
  select(starts_with("boat_length")) %>% 
  na.omit() %>% 
  nrow()

q6a_sum<-survey %>% 
  select(starts_with("boat_length")) %>% 
  group_by(boat_length_m) %>% 
  count() %>% 
  rename("Length (m)"=1, "Count"=2)

q6a_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

#### b. Material
```{r, echo=FALSE}
q6b_response<-survey %>% 
  select(starts_with("boat_material")) %>% 
  na.omit() %>% 
  nrow()

q6b_sum<-survey %>% 
  select(starts_with("boat_material")) %>%
  mutate(boat_material= recode(boat_material,
                             "w"=	"Wood",
                             "fg"=	"Fiberglass")) %>% 
  group_by(boat_material) %>% 
  count() %>%
  rename("Material"=1, "Count"=2)
```
Total Responses = `r q6b_response`

```{r, echo=FALSE}
q6b_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))

```

#### c. Is the boat Motorized?
```{r, echo=FALSE}
q6c_response<-survey %>% 
  select(starts_with("boat_motorized")) %>% 
  na.omit() %>% 
  nrow()

q6c_sum<-survey %>% 
  select(starts_with("boat_motorized")) %>% 
  mutate(boat_motorized= recode(boat_motorized,
                             "y"=	"Yes",
                             "n"=	"No")) %>% 
  group_by(boat_motorized) %>% 
  count() %>%
  rename("Motorized"=1, "Count"=2)
```
Total Responses = `r q6c_response`

```{r, echo=FALSE}
q6c_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

#### d. Is there an onboard power/ electricity source?
```{r, echo=FALSE}
q6d_response<-survey %>% 
  select(starts_with("boat_power")) %>% 
  na.omit() %>% 
  nrow()

q6d_sum<-survey %>% 
  select(starts_with("boat_power")) %>% 
  mutate(boat_power= recode(boat_power,
                             "y"=	"Yes",
                             "n"=	"No")) %>% 
  group_by(boat_power) %>% 
  count() %>%
  rename("Onboard Power"=1, "Count"=2)
```
Total Responses = `r q6d_response`

```{r, echo=FALSE}
q6d_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Comments

### 7. Technology Use 
Please check all the types of technology that you use at least once a week, if any
```{r, echo=FALSE}
q7<-survey %>% 
  select(starts_with("tech")) %>% 
  na.omit()

q7_response <-q7 %>% 
  nrow()

oldnames7<-colnames(q7)
newnames7 <- c("Smart-phone with Internetconnection",
               "Google Maps or other GPSapps",
               "Socialmedia (IG, FB, Twitter)",
               "Other",
               "None")

q7_sum<-q7 %>% 
  rename_at(vars(oldnames7), ~ newnames7)%>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(tech, Count) %>% 
  mutate(Percent = round((Count/q7_response)*100, 0)) %>% 
  rename(Technology = 1)
```
Total Responses = `r q7_response`

```{r, echo=FALSE}
q7_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other
```{r, include=FALSE}
unique(unlist(strsplit(as.character(survey$other_tech), ",")))
```

### 8. Technology Use During Fishing Activity 

Please check all the types of technology that you use or have used at some point for your fishing activity

```{r, echo=FALSE}
q8<-survey %>% 
  select(starts_with("fishtech")) %>% 
  na.omit()

q8_response <-q8 %>% 
  nrow()

oldnames8<-colnames(q8)
newnames8 <- c("VHF Radio",
               "FishFinder (Sonar)",
               "Surveillance Camera",
               "Catch and Data Collection App",
               "Vessel Tracking Technology",
               "GPS",
               "Other",
               "None")

q8_sum<-q8 %>% 
  rename_at(vars(oldnames8), ~ newnames8)%>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(tech, Count) %>% 
  mutate(Percent = round((Count/q8_response)*100, 0)) %>% 
  rename(Technology = 1)
```

Total Responses = `r q8_response`

```{r, echo=FALSE}
q8_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other

```{r, include=FALSE}
q8_other<-unique(unlist(strsplit(as.character(survey$other_fishtech), ",")))
```

*TEXT*
9. What type of tracking technology did you use on your vessel?
*TEXT*
10. Please list some positive aspects of this technology
*TEXT*
11. Please list some negative aspects of this technology
*TEXT*

````
12. You have to install and use one or the other tracking package for a year. which would you be more likely to install and use consistently on every fishing trip?
13. Would you prefer the package you chose or no tracking package at all?
14.i. Would you be willing to pay $5 per month for the package you chose?
14.ii. Would you be willing to pay $10 per month for the package you chose?
14.iii. Would you be willing to pay 15 per month for the package you chose?
14.iv. Would you be willing to pay $20 per month for the package you chose?
15.i. Would you be willing to accept a tracking package for $5 per month?
15.ii. Would you be willing to accept a tracking package for $10 per month?
15.iii. Would you be willing to accept a tracking package for $15 per month?
15.iv. Would you be willing to accept a tracking package for $20 per month?

16. Please mention any negatives that this technology might bring to you
17. Please mention any other positives that this technology might bring to you
````

### 18. Please choose 3 benefits you want from the tracking device, if it is installed in your boat
```{r, echo=FALSE}

```

19. In general, why do you think you and your community may or may not not adopt this technology?

*TEXT*

20. Combining all seasons, what are your top three targeted fisheries?


### 21. Market Distribution of Cacth

What percent of the total catch (out of 100%) goes to...
```{r, echo=FALSE}
q21<-survey %>% 
  select(starts_with("fraction")) %>% 
  mutate(total = rowSums(., na.rm = TRUE))

#calculating number of na values by row
q21_na_count <- apply(q21, 1, function(x) sum(is.na(x)))

#5 indicated entire row was not answered (1 response)
table(q21_na_count) #1 person did not respond to this question

#show distribution of people who answered this question correctly
table(q21$total) #202 correct responses 

#clean df and calculate summary statistics 
q21_clean<-q21 %>% 
  filter(total == 100) %>% 
  replace(., is.na(.), 0) %>% 
  select(-total)

q21_response<-q21_clean %>% 
  nrow()

summary(q21_clean, digits = 1)

#Number of 0 fraction per column 
sapply(q21_clean, function(x)length(which(x==0)))

#number of non-zero fraction per column
sapply(q21_clean, function(x)length(which(x!=0)))
```
Total Responses = `r q21_response` *Number of responses that total 100%

```{r, echo=FALSE}
q21_plot<-q21_clean %>% 
  gather(Market, Fraction) %>% 
  mutate(Market= recode(Market,
                        "fraction_export"=	"Export",
                        "fraction_local_trade"=	"Local Trade",
                        "fraction_neighbor" = "Shared with Neighboring House Hold",
                        "fraction_other" = "Other",
                        "fraction_personal" = "Personal Consumption"))

ggplot(q21_plot, aes(x=Fraction))+
  geom_histogram()+
  facet_grid(. ~ Market)
```

Other

### 22. Are you part of a fishing organization?
```{r, echo=FALSE}
q22_response<-survey %>% 
  select(starts_with("fishing_organization")) %>% 
  na.omit() %>% 
  nrow()

q22_sum<-survey %>% 
  select(starts_with("fishing_organization")) %>% 
  group_by(fishing_organization) %>% 
  count()
```

Total Responses = `r q22_response`

```{r, echo=FALSE}
q22_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### 23. What type of organization?
```{r, echo=FALSE}
q23<-survey %>% 
  filter(fishing_organization=="y") %>% 
  select(starts_with("fishing_org_type"))

#number of responses out of those who indicated they belong to a fishing organization (out of 136)
q23_response<- q23 %>% 
  na.omit() %>% 
  nrow()

q23_sum<-q23 %>% 
  group_by(fishing_org_type) %>% 
  count()
```

Total Responses = `r q23_response`

```{r, echo=FALSE}
q23_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other
### 24. What role do you have in the organization?
```{r, echo=FALSE}
q24<-survey %>% 
  filter(fishing_organization=="y") %>% 
  select(starts_with("fishing_org_role"))

#number of responses out of those who indicated they belong to a fishing organization (out of 136)
q24_response<- q24 %>% 
  na.omit() %>% 
  nrow()

q24_sum<-q24 %>% 
  group_by(fishing_org_role) %>% 
  count()
```

Total Responses = `r q24_response`

```{r, echo=FALSE}
q24_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other

### 25. How many members does the organization have?
```{r, echo=FALSE}
q25<-survey %>% 
  filter(fishing_organization=="y") %>% 
  select(starts_with("fishing_org_members"))

#number of responses out of those who indicated they belong to a fishing organization (out of 136)
q25_response<- q25 %>% 
  na.omit() %>% 
  nrow()

q25_sum<-q25%>% 
  group_by(fishing_org_members) %>% 
  count()
```

Total Responses = `r q25_response`

```{r, echo=FALSE}
q25_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 26. Who is allowed to fish for your #1 targeted fishery, ${target_species_one} ?

```{r, echo=FALSE}
q26_sum<-survey %>% 
  select(starts_with("access")) %>% 
  group_by(access_target_species) %>% 
  count()
```

Total Responses = `r q26_response`

```{r, echo=FALSE}
q26_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


Other
### 27. Please indicate what regulations exist for your #1 targeted fisherie, ${target_species_one}.

```{r, echo=FALSE}
q27_response<-survey %>% 
  select(starts_with("restriction")) %>% 
  na.omit() %>% 
  nrow()

q27_sum<-survey %>% 
  select(starts_with("restriction")) %>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(restriction, count)
```

Total Responses = `r q27_response`

```{r, echo=FALSE}
q27_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other
### 28. Who is responsible for enforcement in your community?
```{r, echo=FALSE}
q28<-survey %>% 
  select(starts_with("enforcement")) %>% 
  select(-enforcement_interval)

q28_response<-q28 %>% 
  na.omit() %>% 
  nrow()

q28_sum<-q28 %>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(enforcement, count)
```

Total Responses = `r q28_response`

```{r, echo=FALSE}
q28_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


Other
### 29. On average, how often are these fishing regulations enforced?

```{r, echo=FALSE}
q29_sum<-survey %>% 
  select(enforcement_interval) %>% 
  group_by(enforcement_interval) %>% 
  count()
```

Total Responses = `r q29_response`

```{r, echo=FALSE}
q29_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other

### 30. Severity of Punishment for Violating Fishing Regulations 

How severe is the punishment when a person gets caught violating the fishing regulations?
```{r, echo=FALSE}
q30<-survey %>% 
  select(punishment_severity) 

q30_response<-q30 %>% 
  na.omit() %>% 
  nrow()

q30_sum<-q30 %>% 
  group_by(punishment_severity) %>% 
  count() %>% 
  rename("Severity"=1, "Count"=2)
```

Total Responses = `r q30_response`

```{r, echo=FALSE}
q30_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 31. Are there any closed areas in your fishing area?

```{r, echo=FALSE}
q31<-survey %>% 
  select(mpa) 

q31_response<-q31 %>% 
  na.omit() %>% 
  nrow()

q31_sum <- q31 %>% 
  mutate(mpa= recode(mpa,
                     "y"=	"Yes",
                     "n"=	"No")) %>% 
  group_by(mpa) %>% 
  count() %>% 
  rename("MPA"=1, "Count"=2)
```

Total Responses = `r q31_response`

```{r, echo=FALSE}
q31_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


32. Wat do you think are the biggest problems your fishery faces?

**TEXT**

33. How do you think the problems you mentioned can be solved?

**TEXT**

### 34. Ranking of Problems During Fishing Activity
Please rank the following problems from 1 to 4, where 1 has the strongest impact on your fishing activity and 4 has the least impact on your fishing activity

```{r, echo=FALSE}
q34<-survey %>% 
  select(starts_with("rank"))

q34_response<-q34 %>% 
  na.omit() %>% 
  nrow()

q34_sum<-q34 %>% 
  gather(rank, problem) %>% 
  count(rank, problem) %>% 
  spread(rank, n) %>% 
  select(problem, rank_one, rank_two, rank_three, rank_four)

#omitting observations with na value in row
q34_sum_omit.na<-q34 %>% 
  na.omit() %>% 
  gather(rank, problem) %>% 
  count(rank, problem) %>% 
  spread(rank, n) %>% 
  select(problem, rank_one, rank_two, rank_three, rank_four)
```


### 35. In the last few years, the current fish catch has…

```{r, echo=FALSE}
q35_sum<-survey %>% 
  select(catch_trends) %>% 
  group_by(catch_trends) %>% 
  count()
```

### 36. How much do you agree with the following statements

```{r, echo=FALSE}
q36<-survey %>% 
  select(starts_with("opinion")) %>% 
  na.omit()

q36_response<-nrow(q36)

q36_sum<-q36 %>% 
  gather(opinion, answer) %>% 
  count(opinion, answer) %>% 
  spread(opinion, n)
```


### 37. Please indicate how much you trust the following groups

```{r, echo=FALSE}
q37<-survey %>% 
  select(starts_with("trust")) %>% 
  na.omit()

q37_response<-nrow(q37)

q37_sum<-q37 %>% 
  gather(trust, answer) %>% 
  count(trust, answer) %>% 
  spread(trust, n)
```


### 38. Please indicate how satisfied you were when working with the following organizations

```{r, echo=FALSE}
q38<-survey %>% 
  select(starts_with("satisfaction")) %>% 
  na.omit()

q38_response<-nrow(q38)

q38_sum<-q38 %>% 
  gather(satisfaction, answer) %>% 
  count(satisfaction, answer) %>% 
  spread(satisfaction, n) %>% 
  replace(., is.na(.), 0)
```

### 39. What is your age?

```{r, echo=FALSE}
q39<-survey %>% 
  select(age) 

q39_count<-q39 %>% 
  group_by(age) %>% 
  count()

#dividing into bins

# set up cut-off values 
breaks <- seq(15, 80, 5)

# bucketing values into bins
age.cut <- cut(q39$age, breaks, right=FALSE)

age.freq <- age.cut %>% 
  table() %>% 
  cbind() %>% 
  as.data.frame() %>% 
  rename(count = 1)
```

### 40. How many years have you been fishing?

```{r, echo=FALSE}
q40<-survey %>% 
  select(years_fishing) %>% 
  na.omit()

q40_response<-q40 %>% 
  nrow()

#dividing into bins

# set up cut-off values 
q40_breaks <- seq(0, 60, 5)

# bucketing values into bins
fishing_cut <- cut(q40$years_fishing, q40_breaks, right=FALSE)

fishing_freq <- fishing_cut %>% 
  table() %>% 
  cbind() %>% 
  as.data.frame() %>% 
  rename(count = 1)
```

**Total Responses** = `r q40_response`

```{r, echo=FALSE}
fishing_freq %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### 41.What is your level of education? (Please choose one)

```{r, echo=FALSE}
q41_response<-survey %>% 
  select(education) %>% 
  na.omit() %>% 
  nrow()

q41_sum<-survey %>% 
  select(education) %>% 
  group_by(education) %>% 
  count()
```

**Total Responses** = `r q41_response`

```{r, echo=FALSE}
q41_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other
### 42. What is your average monthly income?

```{r, echo=FALSE}
q42_response<-survey %>% 
  select(income) %>% 
  na.omit() %>% 
  nrow()
```

**Total Responses** = `r q42_response`

```{r, echo=FALSE}
q42_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


```{r, echo=FALSE}
#set parameters for income break

income_breaks <- seq(0, 100, 10)
```

### 43. What percent (out of 100%) of your annual income comes from fishing?

```{r, echo=FALSE}
q43<-survey %>% 
  select(income_fishing) %>% 
  na.omit()

q43_response<-survey %>% 
  select(income_fishing) %>% 
  na.omit() %>% 
  nrow()

# bucketing values into bins
income_cut <- cut(q43$income_fishing, income_breaks, right=FALSE)

income_freq <- income_cut %>% 
  table() %>% 
  cbind() %>% 
  as.data.frame() %>% 
  rename(count = 1)
```

**Total Responses** = `r q43_response`

```{r, echo=FALSE}
q5_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 44. What percent (out of 100%) of your income is spent on expenses related to fishing?

```{r, echo=FALSE}
q44<-survey %>% 
  select(income_expenses) %>% 
  na.omit()

q44_response<-survey %>% 
  select(income_expenses) %>% 
  na.omit() %>% 
  nrow()

# bucketing values into bins
expenses_cut <- cut(q44$income_expenses, income_breaks, right=FALSE)

expense_freq <- expenses_cut  %>% 
  table() %>% 
  cbind() %>% 
  as.data.frame() %>% 
  rename(count = 1)
```

**Total Responses** = `r q44_response`

```{r, echo=FALSE}
q5_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```



Photo of the Fishing Vessel if available (or other relevant material)
Any additional questions, comments, notes, etc....
