---
title: "Survey Response Distribution"
author: "BR"
date: "28/11/2019"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(DT)
library(kableExtra)
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
```


```{r, include=FALSE}
# Read in all of the raw data
survey <- read_csv("raw/master_survey_resp.csv") %>% 
  mutate(wtp_cat = ifelse(wtr_4 == "n", "pro",
                          ifelse( wtp_1 == "n", "zero",
                                  ifelse(package_nopackage == 1, "pay", "rec")))) %>% 
  mutate(wtp_cat = as.factor(wtp_cat))

header_key <- read_csv("raw/survey_header_key.csv")

choice_key <- read_csv("raw/choice_key.csv") %>% 
  rename(question = 1)

choice_value<- read_csv("raw/choice_value_key.csv") %>% 
  rename(column_header = 1)

#clean choice key for relevant columns in analysis 
qual <- choice_key %>% 
  filter(type == "text") %>% 
  rename(question = 1)

quant <- header_key %>% 
  left_join(choice_key) %>% 
  filter(type!="text")
```

# Results  

```{r, echo=FALSE, warning = FALSE, message = FALSE}
#creating summary df with total response count for each column
totals <- survey %>% 
  gather(column_header,resp) %>% 
  na.omit() %>% 
  group_by(column_header) %>% 
  count() %>% 
  right_join(quant) %>% 
  separate(question, c("question", "sub_question")) %>% 
  mutate(question = as.numeric(question)) %>% 
  arrange(question) %>% 
  na.omit() %>% 
  filter(question != 0) %>% 
  select(question, sub_question, column_header, n) %>% 
  left_join(choice_value)

totals %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

# Section Results  

Question label   

Purpose of Survey  

Survey ID  

Survey Version  

Name of Interviewer  

Affiliated Organization  

1. Country  

2. Community Name  

3. Gender of Interviewed  

## Fisher Characteristics  

### 4. Fishing Gear
In the last 12 months, what fishing gear have you used?
```{r, echo=FALSE}
q4<-survey %>% 
  mutate(gear_buceo = ifelse(grepl("Buceo", other_gear), 1, 0)) %>% 
  select(starts_with("gear")) %>% 
  na.omit() 


oldnames4<-colnames(q4)
newnames4 <- c("Hand Line", "Spear", "Traps", "Stationary Net",  "Mobile Net", "Stationary Line", "Other", "*Buceo")

q4_response<-survey %>% 
  select(starts_with("gear")) %>% 
  na.omit() %>% 
  nrow()

q4_sum<-q4 %>% 
  rename_at(vars(oldnames4), ~ newnames4)%>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(gear, Count) %>% 
#  mutate(Percent = round((Count/q4_response)*100, 0)) %>% 
  rename(Gear = 1) %>% 
  arrange(-Count)
```

**Total Responses** = `r q4_response`

```{r, echo=FALSE}
q4_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

ggplot(q4_sum, aes(x = reorder(Gear, -Count), y = Count)) +
  geom_bar(stat = "identity") +
  xlab("Gear")+
  theme_classic()
```

Other  

```{r}
#Other Gear Indicated 
```

### 5. Vessel Ownership

For fishing purposes, do you own a boat, share a boat, or rent a boat from others, or do not use a boat?
```{r, echo=FALSE}
q5_response<-survey %>% 
  select(starts_with("boat_status")) %>% 
  na.omit() %>% 
  nrow()


q5_sum<-survey %>% 
  select(starts_with("boat_status")) %>%
  mutate(boat_status= recode(boat_status,
                             "own"=	"Own",
                             "share_employee"=	"Share with others as part of a collective",
                             "share_collective"=	"Share with others as an employee",
                             "rent"=	"Rent from others",
                             "none"=	"Do not use a boat to fish")) %>% 
  group_by(boat_status) %>% 
  count() %>%
  rename("Status"=1, "Count"=2)
```

**Total Responses** = `r q5_response`

```{r, echo=FALSE}
q5_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

ggplot(q5_sum, aes(x = reorder(Status, -Count), y = Count)) +
  geom_bar(stat = "identity") +
  xlab("Ownership Status")+
  theme_classic()
```

### 6. Vessel Characteristics
For your primary fishing vessel, please describe the boat in the following aspects:

#### a. Length
```{r, echo=FALSE}
q6a <- survey %>% 
  select(starts_with("boat_length")) %>% 
  na.omit() 

q6a_response<- q6a %>% 
  nrow()

q6a_sum<-survey %>% 
  select(starts_with("boat_length")) %>% 
  group_by(boat_length_m) %>% 
  count() %>% 
  rename("Length (m)"=1, "Count"=2)
```

**Total Responses** = `r q6a_response`

```{r, echo=FALSE}
q6a_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

ggplot(q6a, aes(x = boat_length_m)) +
  geom_histogram(binwidth=5, color="white")+
  xlab("Length (m)")+
  ylab("Count")+
  theme_classic()
```

#### b. Material
```{r, echo=FALSE}
q6b_response<-survey %>% 
  select(starts_with("boat_material")) %>% 
  na.omit() %>% 
  nrow()

q6b_sum<-survey %>% 
  select(starts_with("boat_material")) %>%
  mutate(boat_material= recode(boat_material,
                             "w"=	"Wood",
                             "fg"=	"Fiberglass")) %>% 
  group_by(boat_material) %>% 
  count() %>%
  rename("Material"=1, "Count"=2)
```
**Total Responses** = `r q6b_response`

```{r, echo=FALSE}
q6b_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

#### c. Is the boat Motorized?
```{r, echo=FALSE}
q6c_response<-survey %>% 
  select(starts_with("boat_motorized")) %>% 
  na.omit() %>% 
  nrow()

q6c_sum<-survey %>% 
  select(starts_with("boat_motorized")) %>% 
  mutate(boat_motorized= recode(boat_motorized,
                             "y"=	"Yes",
                             "n"=	"No")) %>% 
  group_by(boat_motorized) %>% 
  count() %>%
  rename("Motorized"=1, "Count"=2)
```
Total Responses = `r q6c_response`

```{r, echo=FALSE}
q6c_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

#### d. Is there an onboard power/ electricity source?
```{r, echo=FALSE}
q6d_response<-survey %>% 
  select(starts_with("boat_power")) %>% 
  na.omit() %>% 
  nrow()

q6d_sum<-survey %>% 
  select(starts_with("boat_power")) %>% 
  mutate(boat_power= recode(boat_power,
                             "y"=	"Yes",
                             "n"=	"No")) %>% 
  group_by(boat_power) %>% 
  count() %>%
  rename("Onboard Power"=1, "Count"=2)
```
Total Responses = `r q6d_response`

```{r, echo=FALSE}
q6d_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

Comments

### 7. Technology Use 
Please check all the types of technology that you use at least once a week, if any
```{r, echo=FALSE}
q7<-survey %>% 
  select(starts_with("tech")) %>% 
  na.omit()

q7_response <-q7 %>% 
  nrow()

oldnames7<-colnames(q7)
newnames7 <- c("Smart-phone with Internetconnection",
               "Google Maps or other GPSapps",
               "Socialmedia (IG, FB, Twitter)",
               "Other",
               "None")

q7_sum<-q7 %>% 
  rename_at(vars(oldnames7), ~ newnames7)%>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(tech, Count) %>% 
  mutate(Percent = round((Count/q7_response)*100, 0)) %>% 
  rename(Technology = 1)
```

**Total Responses** = `r q7_response`  

```{r, echo=FALSE}
q7_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other  

```{r, include=FALSE}
unique(unlist(strsplit(as.character(survey$other_tech), ",")))
```

### 8. Fishing Technology Use 

Please check all the types of technology that you use or have used at some point for your fishing activity

```{r, echo=FALSE}
q8<-survey %>% 
  select(starts_with("fishtech")) %>% 
  na.omit()

q8_response <-q8 %>% 
  nrow()

oldnames8<-colnames(q8)
newnames8 <- c("VHF Radio",
               "FishFinder (Sonar)",
               "Surveillance Camera",
               "Catch and Data Collection App",
               "Vessel Tracking Technology",
               "GPS",
               "Other",
               "None")

q8_sum<-q8 %>% 
  rename_at(vars(oldnames8), ~ newnames8)%>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(tech, Count) %>% 
  mutate(Percent = round((Count/q8_response)*100, 0)) %>% 
  rename(Technology = 1)
```

**Total Responses** = `r q8_response`

```{r, echo=FALSE}
q8_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other  

*TEXT*

```{r, include=FALSE}
q8_other<-unique(unlist(strsplit(as.character(survey$other_fishtech), ",")))
```



9. What type of tracking technology did you use on your vessel?
*TEXT*
10. Please list some positive aspects of this technology
*TEXT*
11. Please list some negative aspects of this technology
*TEXT*

## Choice Experiment  

12. You have to install and use one or the other tracking package for a year. which would you be more likely to install and use consistently on every fishing trip?

13. Would you prefer the package you chose or no tracking package at all?
14.i. Would you be willing to pay $5 per month for the package you chose?
14.ii. Would you be willing to pay $10 per month for the package you chose?
14.iii. Would you be willing to pay 15 per month for the package you chose?
14.iv. Would you be willing to pay $20 per month for the package you chose?
15.i. Would you be willing to accept a tracking package for $5 per month?
15.ii. Would you be willing to accept a tracking package for $10 per month?
15.iii. Would you be willing to accept a tracking package for $15 per month?
15.iv. Would you be willing to accept a tracking package for $20 per month?

16. Please mention any negatives that this technology might bring to you
17. Please mention any other positives that this technology might bring to you


### 18. Desired Benefits

Please choose 3 benefits you want from the tracking device, if it is installed in your boat
```{r, echo=FALSE}

```

19. In general, why do you think you and your community may or may not not adopt this technology?

*TEXT*

## Catch  

20. Combining all seasons, what are your top three targeted fisheries?


### 21. Market Distribution  

What percent of the total catch (out of 100%) goes to...
```{r, echo=FALSE}
q21<-survey %>% 
  select(starts_with("fraction")) %>% 
  mutate(total = rowSums(., na.rm = TRUE))

#calculating number of na values by row
q21_na_count <- apply(q21, 1, function(x) sum(is.na(x)))

#5 indicated entire row was not answered (1 response)
table(q21_na_count) #1 person did not respond to this question

#show distribution of people who answered this question correctly
table(q21$total) #202 correct responses 

#clean df and calculate summary statistics 
q21_clean<-q21 %>% 
  filter(total == 100) %>% 
  replace(., is.na(.), 0) %>% 
  select(-total)

q21_response<-q21_clean %>% 
  nrow()

summary(q21_clean, digits = 1)

#Number of 0 fraction per column 
sapply(q21_clean, function(x)length(which(x==0)))

#number of non-zero fraction per column
sapply(q21_clean, function(x)length(which(x!=0)))
```
**Total Responses** = `r q21_response` *Number of responses that total 100%

```{r, echo=FALSE}
q21_plot<-q21_clean %>% 
  gather(Market, Fraction) %>% 
  mutate(Market= recode(Market,
                        "fraction_export"=	"Export",
                        "fraction_local_trade"=	"Local Trade",
                        "fraction_neighbor" = "Shared with Neighboring House Hold",
                        "fraction_other" = "Other",
                        "fraction_personal" = "Personal Consumption"))

ggplot(q21_plot, aes(x=Fraction))+
  geom_histogram()+
  facet_grid(. ~ Market)
```

Other

## Fishing Organization  

### 22. Membership 

Are you part of a fishing organization?
```{r, echo=FALSE}
q22_response<-survey %>% 
  select(starts_with("fishing_organization")) %>% 
  na.omit() %>% 
  nrow()

q22_sum<-survey %>% 
  select(starts_with("fishing_organization")) %>%
  mutate(fishing_organization= recode(fishing_organization,
                             "y"=	"Yes",
                             "n"=	"No")) %>%   
  group_by(fishing_organization) %>% 
  count() %>% 
  rename("Membership" = 1, "Count" = 2)
```

**Total Responses** = `r q22_response`

```{r, echo=FALSE}
q22_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### 23. Organization Type  

What type of organization?
```{r, echo=FALSE}
q23<-survey %>% 
  filter(fishing_organization=="y") %>% 
  select(starts_with("fishing_org_type")) %>% 
  na.omit()

#number of responses out of those who indicated they belong to a fishing organization (out of 136)
q23_response<- q23 %>% 
  nrow()

q23_sum<-q23 %>%
  mutate(fishing_org_type = recode(fishing_org_type,
                             "cooperative"=	"Cooperative",
                             "union"=	"Union",
                             "customary_org" = "Customary Organization",
                             "other" = "Other")) %>%   
  group_by(fishing_org_type) %>% 
  count() %>% 
  rename("Type of Organization" = 1, "Count" = 2)
```

**Total Responses** = `r q23_response`

```{r, echo=FALSE}
q23_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other  

### 24. Role in Organization 

What role do you have in the organization?
```{r, echo=FALSE}
q24<-survey %>% 
  filter(fishing_organization=="y") %>% 
  select(starts_with("fishing_org_role")) %>% 
  na.omit()

#number of responses out of those who indicated they belong to a fishing organization (out of 136)
q24_response<- q24 %>% 
  nrow()

q24_sum<-q24 %>% 
  mutate(fishing_org_role = recode(fishing_org_role,
                             "apprentice" =	"Apprentice",
                             "partner" =	"Partner",
                             "director" =	"Director",
                             "other"	= "Other")) %>%   
  group_by(fishing_org_role) %>% 
  count() %>% 
  rename("Role in Organization" = 1, "Count" = 2)
```

**Total Responses** = `r q24_response`

```{r, echo=FALSE}
q24_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other  

### 25. Organization Size   

How many members does the organization have?
```{r, echo=FALSE}
q25<-survey %>% 
  filter(fishing_organization=="y") %>% 
  select(starts_with("fishing_org_members")) %>% 
  na.omit()

#number of responses out of those who indicated they belong to a fishing organization (out of 136)
q25_response<- q25 %>% 
  nrow()

q25_sum<- q25 %>% 
  mutate(fishing_org_members = recode(fishing_org_members,
                             "apprentice" =	"Apprentice",
                             "partner" =	"Partner",
                             "director" =	"Director",
                             "other"	= "Other")) %>%   
  group_by(fishing_org_members) %>% 
  count() %>% 
  rename("Members in Organization" = 1, "Count" = 2)
```

**Total Responses** = `r q25_response`

```{r, echo=FALSE}
q25_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Governance

### 26. Access to Fishery  

Who is allowed to fish for your #1 targeted fishery?

```{r, echo=FALSE}
q26<-survey %>% 
  select(access_target_species) %>% 
  na.omit()

q26_response <- q26 %>% 
  nrow()

q26_sum<-q26 %>% 
  mutate(access_target_species = recode(access_target_species,
                             "community" =	"Members of your fishing organization/ community only",
                             "neighboring_community" =	"Members from you and neighboring fishing organization/ communities",
                             "no_restrictions" =	"Open Access / No Restrictions",
                             "permit_holders"	= "Anyone with a Permit",
                             "other" = "Other")) %>%   
  group_by(access_target_species) %>% 
  count() %>% 
  rename("Access to Target Species" = 1, "Count" = 2)
```

**Total Responses** = `r q26_response`

```{r, echo=FALSE}
q26_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


Other  

### 27. Regulations  

Please indicate what regulations exist for your #1 targeted fisherie.

```{r, echo=FALSE}
q27<- survey %>% 
  select(starts_with("restriction")) %>% 
  na.omit() 

q27_response<- q27 %>% 
  nrow()

oldnames27 <-colnames(q27)
newnames27 <- c("Gear", "Size", "Seasonal", "Spacial", "Quota", "Other", "No Restrictions")

q27_sum<-q27 %>%
  rename_at(vars(oldnames27), ~ newnames27) %>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(restriction, count) %>% 
  rename("Restriction Type" = 1, "Count" = 2)
```

**Total Responses** = `r q27_response`

```{r, echo=FALSE}
q27_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other  

### 28. Enforcement  

Who is responsible for enforcement in your community?
```{r, echo=FALSE}
q28<-survey %>% 
  select(starts_with("enforcement")) %>% 
  select(-enforcement_interval) %>% 
  na.omit()

q28_response<-q28 %>% 
  nrow()

oldnames28<-colnames(q28)
newnames28 <- c("Community Members", "Village Customary Leaders", "Village Government", "Provincial Government", "National Government", "No Enforcement", "Other")

q28_sum<-q28 %>%
  rename_at(vars(oldnames28), ~ newnames28) %>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  gather(enforcement, count) %>% 
  rename("Enforcement Official" = 1, "Count" = 2)
```

**Total Responses** = `r q28_response`

```{r, echo=FALSE}
q28_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


Other  

### 29. Enforcement Frequency  

On average, how often are these fishing regulations enforced?

```{r, echo=FALSE}
q29<-survey %>% 
  select(enforcement_interval) %>% 
  na.omit()

q29_response<-q29 %>% 
  nrow()

q29_sum<-q29 %>% 
  mutate(enforcement_interval = recode(enforcement_interval,
                             "once_week" =	"Once per Week",
                             "once_month" =	"Once per Month",
                             "few_year" =	"Few Times per Year",
                             "once_year"	= "Once per Year",
                             "never" = "No Enforcement",
                             "other" = "Other",
                             "every_week" = "Every Week")) %>%   
  group_by(enforcement_interval) %>% 
  count() %>% 
  rename("Enforcement Interval"=1, "Count"=2)
```

**Total Responses** = `r q29_response`

```{r, echo=FALSE}
q29_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other  

### 30. Severity of Punishment  

How severe is the punishment when a person gets caught violating the fishing regulations?
```{r, echo=FALSE}
q30<-survey %>% 
  select(punishment_severity) %>% 
  na.omit()

q30_response<-q30 %>% 
  nrow()

q30_sum<-q30 %>%
  mutate(punishment_severity = recode(punishment_severity,
                             "moderate" =	"Moderate",
                             "none" =	"No Punishment",
                             "severe" =	"Severe",
                             "strong"	= "Strong",
                             "weak" = "Weak")) %>%   
  group_by(punishment_severity) %>% 
  count() %>% 
  rename("Severity"=1, "Count"=2)
```

**Total Responses** = `r q30_response`

```{r, echo=FALSE}
q30_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 31. Closed Areas    

Are there any closed areas in your fishing area?

```{r, echo=FALSE}
q31<-survey %>% 
  select(mpa) 

q31_response<-q31 %>% 
  na.omit() %>% 
  nrow()

q31_sum <- q31 %>% 
  mutate(mpa= recode(mpa,
                     "y"=	"Yes",
                     "n"=	"No")) %>% 
  group_by(mpa) %>% 
  count() %>% 
  rename("MPA"=1, "Count"=2)
```

**Total Responses** = `r q31_response`

```{r, echo=FALSE}
q31_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


32. Wat do you think are the biggest problems your fishery faces?

**TEXT**

33. How do you think the problems you mentioned can be solved?

**TEXT**

## Perception  

### 34. Rank: Fishing Problems  

Please rank the following problems from 1 to 4, where 1 has the strongest impact on your fishing activity and 4 has the least impact on your fishing activity

```{r, echo=FALSE}
q34<-survey %>% 
  select(starts_with("rank"))

q34_response<-q34 %>% 
  na.omit() %>% 
  nrow()

q34_sum<-q34 %>% 
  gather(rank, problem) %>% 
  count(rank, problem) %>% 
  spread(rank, n) %>% 
  select(problem, rank_one, rank_two, rank_three, rank_four)

#omitting observations with na value in row
q34_sum_omit.na<-q34 %>% 
  na.omit() %>% 
  gather(rank, problem) %>% 
  count(rank, problem) %>% 
  spread(rank, n) %>% 
  select(problem, rank_one, rank_two, rank_three, rank_four) %>% 
  arrange(-rank_one) %>% 
  rename("Problem"=1, "Rank 1"=2, "Rank 2" = 3, "Rank 3"=4, "Rank 4" = 5) %>% 
  mutate(Problem = recode(Problem,
                          "corruption"=	"Corruption of Fishing Authorities",
                          "iuu"=	"Illegal Fishing",
                          "pollution" = "Marine Trash and Pollution",
                          "weather" = "Extreme Weather Events")) 
```

**Total Responses** = `r q34_response`

```{r, echo=FALSE}
q34_sum_omit.na %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### 35. Catch Trends  

In the last few years, the current fish catch has…

```{r, echo=FALSE}
q35<-survey %>% 
  select(catch_trends) %>% 
  na.omit() 

q35_response <- q35 %>%
  nrow()
  
q35_sum<-q35 %>% 
  mutate(catch_trends = recode(catch_trends,
                        "improve_high"=	"Improved a Lot",
                        "improve_low"=	"Improved a Little",
                        "no_change" = "Stayed the Same",
                        "decline_low" = "Declined a Little",
                        "decline_high" = "Declined a Lot")) %>% 
  group_by(catch_trends) %>% 
  count() %>% 
  rename("Trend" = 1, "Count" = 2)
```

**Total Responses** = `r q35_response`

```{r, echo=FALSE}
q35_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Opinion  

### 36. Statements  

How much do you agree with the following statements

```{r, echo=FALSE}
q36<-survey %>% 
  select(starts_with("opinion")) %>% 
  na.omit()

q36_response<-q36 %>% 
  nrow()

q36_sum<-q36 %>% 
  gather(opinion, answer) %>% 
  count(opinion, answer) %>% 
  spread(answer, n) %>% 
  rename("Statement" = 1,
         "Strongly Disagree" = 2, 
         "Disagree" = 3, 
         "Neutral" = 4, 
         "Agree" = 5, 
         "Strongly Agree" = 6)
```

**Total Responses** = `r q36_response`

```{r, echo=FALSE}
q36_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### 37. Groups  

Please indicate how much you trust the following groups

```{r, echo=FALSE}
q37<-survey %>% 
  select(starts_with("trust")) %>% 
  na.omit()

q37_response<-nrow(q37)

q37_sum<-q37 %>% 
  gather(trust, answer) %>% 
  count(trust, answer) %>% 
  spread(answer, n)%>% 
  rename("Group" = 1,
         "Distrust Entirely" = 2, 
         "Distrust" = 3, 
         "Neutral" = 4, 
         "Trust" = 5, 
         "Trust Entirely" = 6)
```

**Total Responses** = `r q37_response`

```{r, echo=FALSE}
q37_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 38. Organizations  

Please indicate how satisfied you were when working with the following organizations

```{r, echo=FALSE}
q38<-survey %>% 
  select(starts_with("satisfaction")) %>% 
  na.omit()

q38_response<-nrow(q38)

q38_sum<-q38 %>% 
  gather(satisfaction, answer) %>% 
  count(satisfaction, answer) %>% 
  spread(answer, n) %>% 
  replace(., is.na(.), 0) %>%
  rename("Organization" = 1,
         "N/A" = 2, 
         "Extremely Unsatisfied" = 3, 
         "Unsatisfied" = 4, 
         "Neutral" = 5, 
         "Satisfied" = 6,
         "Extremely Satisfied" = 7)
  
```

**Total Responses** = `r q38_response`

```{r, echo=FALSE}
q38_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Demographics  

### 39. Age

What is your age?

```{r, echo=FALSE}
q39<-survey %>% 
  select(age) %>% 
  na.omit()

q39_response<-nrow(q39)

q39_count<-q39 %>% 
  group_by(age) %>% 
  count()

#dividing into bins

# set up cut-off values 
breaks <- seq(15, 80, 5)

# bucketing values into bins
age_cut <- cut(q39$age, breaks, right=FALSE)

age_freq <- age_cut %>% 
  table() %>% 
  cbind() %>% 
  as.data.frame() %>% 
  rename(Count = 1)

q39_sum<-age_freq %>% 
  mutate("Age Group" = rownames(age_freq)) %>% 
  select("Age Group", "Count")
```

**Total Responses** = `r q39_response`

```{r, echo=FALSE}
q39_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 40. Fishing Experience  

How many years have you been fishing?

```{r, echo=FALSE}
q40<-survey %>% 
  select(years_fishing) %>% 
  na.omit()

q40_response<-q40 %>% 
  nrow()

#dividing into bins

# set up cut-off values 
q40_breaks <- seq(0, 60, 5)

# bucketing values into bins
fishing_cut <- cut(q40$years_fishing, q40_breaks, right=FALSE)

fishing_freq <- fishing_cut %>% 
  table() %>% 
  cbind() %>% 
  as.data.frame() %>% 
  rename(Count = 1)

q40_sum <- fishing_freq %>% 
  mutate("Years Group" = rownames(fishing_freq)) %>% 
  select("Years Group", "Count")
```

**Total Responses** = `r q40_response`

```{r, echo=FALSE}
q40_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### 41. Education  

What is your level of education? (Please choose one)

```{r, echo=FALSE}
q41 <- survey %>% 
  select(education) %>% 
  na.omit()

q41_response <- q41 %>% 
  nrow()

q41_sum <- q41 %>% 
  mutate(education = recode(education,
                        "no_formal"=	"No Formal Education",
                        "other"=	"Other",
                        "primary" = "Primary School",
                        "secondary" = "Secondary / High School",
                        "university" = "College / University",
                        "vocational" = "Vocational Training / Trade School")) %>% 
  group_by(education) %>% 
  count() %>% 
  rename("Education Level" = 1, "Count" = 2)
```

**Total Responses** = `r q41_response`

```{r, echo=FALSE}
q41_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Other  

### 42. Income  

What is your average monthly income?

```{r, echo=FALSE}
q42<-survey %>% 
  select(income) %>% 
  na.omit()

q42_response<-q42 %>% 
  nrow()

q42_sum<- q42 %>% 
  summarise(mean = mean(income), n = n())
```

**Total Responses** = `r q42_response`

```{r, echo=FALSE}
q42_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


```{r, echo=FALSE}
#set parameters for income break

income_breaks <- seq(0, 100, 10)
```

### 43. Percent Income - Fishing

What percent (out of 100%) of your annual income comes from fishing?

```{r, echo=FALSE}
q43<-survey %>% 
  select(income_fishing) %>% 
  na.omit()

q43_response<-survey %>% 
  select(income_fishing) %>% 
  na.omit() %>% 
  nrow()

# bucketing values into bins
income_cut <- cut(q43$income_fishing, income_breaks, right=FALSE)

income_freq <- income_cut %>% 
  table() %>% 
  cbind() %>% 
  as.data.frame() %>% 
  rename(Count = 1)

q43_sum <- income_freq %>% 
  mutate("Percent Income from Fishing" = rownames(income_freq)) %>% 
  select("Percent Income from Fishing", "Count")
```

**Total Responses** = `r q43_response`

```{r, echo=FALSE}
q43_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 44. Percent Income - Expenses  

What percent (out of 100%) of your income is spent on expenses related to fishing?

```{r, echo=FALSE}
q44<-survey %>% 
  select(income_expenses) %>% 
  na.omit()

q44_response<-survey %>% 
  select(income_expenses) %>% 
  na.omit() %>% 
  nrow()

# bucketing values into bins
expenses_cut <- cut(q44$income_expenses, income_breaks, right=FALSE)

expense_freq <- expenses_cut  %>% 
  table() %>% 
  cbind() %>% 
  as.data.frame() %>% 
  rename(Count = 1)

q44_sum <- expense_freq %>% 
  mutate("Percent Income on Expenses" = rownames(expense_freq)) %>% 
  select("Percent Income on Expenses", "Count")
```

**Total Responses** = `r q44_response`

```{r, echo=FALSE}
q44_sum %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```



Photo of the Fishing Vessel if available (or other relevant material)
Any additional questions, comments, notes, etc....

# Basic CE Related Numbers  

```{r}
library(mlogit)
data("Electricity", package = "mlogit")

Electr <- mlogit.data(Electricity, id="id", choice="choice", varying=3:26, shape="wide", sep="")

```
