---
title: "Demographic Distribution"
author: "BR"
date: "28/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(DT)
```


```{r}
# Read in all of the raw data
survey <- read_csv("raw/master_survey_resp.csv")
```
Question label 
Purpose of Survey
Survey ID
Survey Version
Name of Interviewer
Affiliated Organization
1. Country
2. Community Name
3. Gender of Interviewed


4. In the last 12 months, what fishing gear have you used?
```{r}
q4_response<-survey %>% 
  select(starts_with("gear")) %>% 
  na.omit() %>% 
  nrow()

q4_sum<-survey %>% 
  mutate(gear_buceo = ifelse(grepl("Buceo", other_gear), 1, 0)) %>% 
  select(starts_with("gear")) %>% 
  summarise_all(sum, na.rm = TRUE)
```


Other

5. For fishing purposes, do you own a boat, share a boat, or rent a boat from others, or do not use a boat?
```{r}
q5_response<-survey %>% 
  select(starts_with("boat_status")) %>% 
  na.omit() %>% 
  nrow()

q5_sum<-survey %>% 
  select(starts_with("boat_status")) %>% 
  group_by(boat_status) %>% 
  count()
```

6. For your primary fishing vessel, please describe the boat in the following aspects:

a. Length
```{r}
q6a_response<-survey %>% 
  select(starts_with("boat_length")) %>% 
  na.omit() %>% 
  nrow()

q6a_sum<-survey %>% 
  select(starts_with("boat_length")) %>% 
  group_by(boat_length_m) %>% 
  count()
```

b. Material
```{r}
q6b_response<-survey %>% 
  select(starts_with("boat_material")) %>% 
  na.omit() %>% 
  nrow()

q6b_sum<-survey %>% 
  select(starts_with("boat_material")) %>% 
  group_by(boat_material) %>% 
  count()
```

c. Is the boat motorized
```{r}
q6c_response<-survey %>% 
  select(starts_with("boat_motorized")) %>% 
  na.omit() %>% 
  nrow()

q6c_sum<-survey %>% 
  select(starts_with("boat_motorized")) %>% 
  group_by("boat_motorized") %>% 
  count()
```

d. Is there an onboard power/ electricity source?
```{r}
q6d_response<-survey %>% 
  select(starts_with("boat_power")) %>% 
  na.omit() %>% 
  nrow()

q6d_sum<-survey %>% 
  select(starts_with("boat_power")) %>% 
  group_by(boat_power) %>% 
  count()
```

Comments

7. Please check all the types of technology that you use at least once a week, if any
```{r}
unique(unlist(strsplit(as.character(survey$other_tech), ",")))

q7_response<-survey %>% 
  select(starts_with("tech")) %>% 
  na.omit() %>% 
  nrow()

q7_sum<-survey %>% 
  select(starts_with("tech")) %>% 
  summarise_all(sum, na.rm = TRUE)
```


Other

8. Please check all the types of technology that you use or have used at some point for your fishing activity
```{r}
q8_response<-survey %>% 
  select(starts_with("fishtech")) %>% 
  na.omit() %>% 
  nrow()

q8_sum<-survey %>% 
  select(starts_with("fishtech")) %>% 
  summarise_all(sum, na.rm = TRUE)

q8_other<-unique(unlist(strsplit(as.character(survey$other_fishtech), ",")))
```

Other
*TEXT*
9. What type of tracking technology did you use on your vessel?
*TEXT*
10. Please list some positive aspects of this technology
*TEXT*
11. Please list some negative aspects of this technology
*TEXT*

````
12. You have to install and use one or the other tracking package for a year. which would you be more likely to install and use consistently on every fishing trip?
13. Would you prefer the package you chose or no tracking package at all?
14.i. Would you be willing to pay $5 per month for the package you chose?
14.ii. Would you be willing to pay $10 per month for the package you chose?
14.iii. Would you be willing to pay 15 per month for the package you chose?
14.iv. Would you be willing to pay $20 per month for the package you chose?
15.i. Would you be willing to accept a tracking package for $5 per month?
15.ii. Would you be willing to accept a tracking package for $10 per month?
15.iii. Would you be willing to accept a tracking package for $15 per month?
15.iv. Would you be willing to accept a tracking package for $20 per month?

16. Please mention any negatives that this technology might bring to you
17. Please mention any other positives that this technology might bring to you
````

18. Please choose 3 benefits you want from the tracking device, if it is installed in your boat
```{r}

```

19. In general, why do you think you and your community may or may not not adopt this technology?

*TEXT*

20. Combining all seasons, what are your top three targeted fisheries?


21. What percent of the total catch (out of 100%) goes to...
```{r}
q21_response<-survey %>% 
  select(starts_with("fraction")) %>% 
  mutate(fraction_total = rowSums(.))

  na.omit() %>% 
  nrow()

q21_sum<-survey %>% 
  select(starts_with("fishtech")) %>% 
  summarise_all(sum, na.rm = TRUE)
```




Other
22. Are you part of a fishing organization?
23. What type of organization?
Other
24. What role do you have in the organization?
Other
25. How many members does the organization have?
26. Who is allowed to fish for your #1 targeted fishery, ${target_species_one} ?
Other
27. Please indicate what regulations exist for your #1 targeted fisherie, ${target_species_one}.
Other
28. Who is responsible for enforcement in your community?
Other
29. On average, how often are these fishing regulations enforced?
Other
30. How severe is the punishment when a person gets caught violating the fishing regulations?
31. Are there any closed areas in your fishing area?
32. Wat do you think are the biggest problems your fishery faces?


33. How do you think the problems you mentioned can be solved?


34. Please rank the following problems from 1 to 4, where 1 has the strongest impact on your fishing activity and 4 has the least impact on your fishing activity



35. In the last few years, the current fish catch has…
36. How much do you agree with the following statements








37. Please indicate how much you trust the following groups











38. Please indicate how satisfied you were when working with the following organizations


39. What is your age?
40. How many years have you been fishing?
41.What is your level of education? (Please choose one)
Other
42. What is your average monthly income?
43. What percent (out of 100%) of your annual income comes from fishing?
44. What percent (out of 100%) of your income is spent on expenses related to fishing?
Photo of the Fishing Vessel if available (or other relevant material)
Any additional questions, comments, notes, etc....
