---
title: "mlogit"
author: "Panga Watch"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(mlogit)
variables <- read.csv("int/variables.csv", stringsAsFactors = TRUE)
```

```{r}
# try mlogit with pooled
pooled <- read_csv("int/pooled_data_fix.csv") %>%
  select(-STR) %>%
  left_join(variables, by = "survey_id") %>%
  select(-noalt) #read in pooled data
  

map_column <- rep(c("A","B"),length(unique(pooled$survey_id))) # make a column which denotes the alternative, "A" or "B"

# map_column <- rep(c("A"),length(unique(pooled$survey_id))*2)

pooled_mlogit_data <- pooled %>%
  #select(-ASC, -9:-12) %>%
  mutate(alt = map_column,
         choiceid = survey_id,
         choice = ifelse(RES == 1, "TRUE", "FALSE")) %>%
  select(-RES) %>%
  rename("id" = "survey_id") %>%
  mutate(sos = as.factor(sos), info = as.factor(info), own = as.factor(own), choice = as.logical(choice))

pooled_mlogit_data_final <- mlogit.data(pooled_mlogit_data, shape = "long", choice = "choice", alt.var = "alt", id = "id") #put data into format that can work with mlogit

pooled_mlogit_data_final <- within(pooled_mlogit_data_final, own <- relevel(own, ref = 4)) # set reference level for data ownership to public access

m_pooled <- mlogit(choice ~ sos + info + own | -1, pooled_mlogit_data_final) # run the model with choice experiment only. -1 removes the intercept. 

summary(m_pooled) #only pooled attributes mlogit model.. produces same results as clogit only pooled attributes

```

Attempt to add characteristics into the model 
 - Having issues with this, because it is now giving us estimates based on the two options we gave them.  - 2:intercept is the beta value associated with each 2nd option offered I believe. This is happening because not all options are the same, therefore there must be a interaction term. 
```{r}
m_pooled_char <- mlogit(choice ~ sos + info + own | community + education, pooled_mlogit_data_final) ## is this correctly adding attributes to model?? It is comparing to each alternative offerred....
summary(m_pooled_char)

fitted(m_pooled_char)
```

Try to add in the opt out to use with mlogit
 - Has not proven to be successful yet.
 - Idea: Could we treat the opt out as no sos, anonymous, and owned by fishermen? The "status quo". This way we could just code the mlogit as having the third option always be the status quo, instead of trying to incorporate an optout column. 
```{r}
## try standard with mlogit... not working. See this stack overflow for how to supposedely incorporate an opt out with mlogit() : https://stackoverflow.com/questions/31355145/including-opt-out-as-alternative-specific-constant-in-r-mlogit

## did not work trying to exclude 3rd option. I.e. present the data with two options, but both could have choice == FALSE. 

## Try making the optout the status quo and present that as a 3rd choice, "C"?

standard_opt_out <- read_csv("int/standard_opt_out_fix.csv") %>%
  select(-STR, -noalt) %>%
  left_join(variables, by = "survey_id") #%>%
  #filter(ASC != 0) 
  

map_column <- rep(c("A","B", "C"),length(unique(standard_opt_out$survey_id))) # make a column of A,B,C to denote the three choices offered... i.e. package A, package B, opt out.
#map_column <- rep(c("A","B"),length(unique(standard_opt_out$survey_id)))

standard_mlogit_data <- standard_opt_out %>%
  select(-interviewer, -interviewer_Org) %>%
  mutate(alt = map_column,
         choiceid = survey_id,
         choice = ifelse(RES == 1, "TRUE", "FALSE")) %>%
  rename("id" = "survey_id") %>%
  mutate(sos = as.factor(sos), info = as.factor(info), own = as.factor(own), choice = as.logical(choice)) 

standard_mlogit_data$optout <- factor(ifelse(standard_mlogit_data$alt == "C", "1", "0")) # add the alternative specific constant which denotes the opt out choice

standard_mlogit_data_final <- mlogit.data(standard_mlogit_data, shape = c("long"), choice = "choice", alt.var = "alt", id.var  = "id") #put data into format that can work with mlogit

standard_mlogit_data_final <- within(standard_mlogit_data_final, own <- relevel(own, ref = 4)) #change reference level for ownership variable. 

standard_mlogit <- mlogit(choice ~ sos + info + own | -1, standard_mlogit_data_final)

summary(standard_mlogit)

packages <- read_csv("raw/packages.csv") %>%
   mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,0,1))
```



Attempt to extract probabilities out of pooled model
 - using fitted() to get fitted probability values... produces different results than just calculating ourselves by plugging into model output formula. See below. 
 - I think the fitted() function produces fitted probabilities of a package vs another package, while just plugging into our equation, we get the probabilities based on the attribute levels and not packages.
 - Linear predictors given by mlogit model are the same as just plugging into model. Use these instead of creating a function, since it would just be the same as clogit function that we made. 
 
```{r}
fitted <- data.frame(probs = fitted(m_pooled, outcome = FALSE), id_fit = 1:211, lin_pred = m_pooled$linpred) # this shows all of the predicted probabilities for each of the choices offered apparently... 
fitted_1 <- fitted %>%
  select(id_fit, probs = probs.A, lin_pred = lin_pred.A)
fitted_2 <- fitted %>%
  select(id_fit, probs = probs.B, lin_pred = lin_pred.B)

fitted_join <- rbind(fitted_1, fitted_2) %>%
  arrange(id_fit)

new <- pooled_mlogit_data %>%
  select(package, STR.y, info, sos, own)

model_preds <- cbind(new, fitted_join) %>%
  mutate(lin_pred_probs = exp(lin_pred)/(1+ exp(lin_pred))) 
  #filter(package == 4) ## i think we should use lin_pred instead of fitted values for probabilities...

model_preds %>%
  filter(STR.y != id_fit) # we good

preds_pooled <- model_preds %>%
  group_by(package, info, sos, own) %>%
  summarise(probs = mean(probs), lin_pred_probs = mean(lin_pred_probs))

write.csv(preds_pooled, "output/mlogit_pooled_probs.csv", row.names = FALSE)

```


**Make pooled predictions using linear predictors given from model and calculate marginal probabilities based off of the status quo and GFW tech**
```{r}

# the status quo probability; Anonymous (info = 0), No SOS (sos = 0), Owned by fishermen (own = 1)
(status_quo <- preds_pooled$lin_pred_probs[preds_pooled$package == 15])
#0.7693023

## Make status quo non-anonymous; Non-Anonymous (info = 1), No SOS (sos = 0), Owned by fishermen (own = 1)
add_non_anon <- preds_pooled$lin_pred_probs[preds_pooled$package == 3]
#0.7451011

## Make status quo with SOS; Anonymous (info = 0), SOS (sos = 1), Owned by fishermen (own = 1)
add_sos <- preds_pooled$lin_pred_probs[preds_pooled$package == 7]

## Make status quo own by ind; Anonymous (info = 0), no SOS (sos = 0), Owned by industry (own = 2)
add_own_by_ind <- preds_pooled$lin_pred_probs[preds_pooled$package == 10]

## Make status quo own by gov; Anonymous (info = 0), no SOS (sos = 0), Owned by government (own = 3)
add_own_by_gov <- preds_pooled$lin_pred_probs[preds_pooled$package == 6]

## Make status quo own by public; Anonymous (info = 0), no SOS (sos = 0), Owned by public (own = 4)
add_own_by_public <- preds_pooled$lin_pred_probs[preds_pooled$package == 5]

### Adding non anon to status quo results in a 2.42011% decrease
lin_pred_add_non_anon <-  status_quo - add_non_anon

### adding sos to status quo results in a 20.559205227% increase
lin_pred_add_sos <- status_quo - add_sos

### adding industry ownership results in a 34.70097% decrease
lin_pred_add_ind <- status_quo - add_own_by_ind

### adding government ownership results in a 0.3976773% increase
lin_pred_add_gov <- status_quo - add_own_by_gov

### adding public access results in a 26.93022% decrease
lin_pred_add_public <- status_quo - add_own_by_public


# the status quo GFW probability; Non-Anonymous (info = 1), SOS (sos = 1), Public access (own = 4)
GFW_prob <- preds_pooled$lin_pred_probs[preds_pooled$package == 11]
#0.91077

# GFW probabilty with anonymous; Anonymous (info = 0), SOS (sos = 1), Public (own = 4)
add_anon_GFW <- preds_pooled$lin_pred_probs[preds_pooled$package == 4]

# GFW probabilty with no SOS; non Anonymous (info = 1), no SOS (sos = 0), Public (own = 4)
add_no_sos_GFW <- preds_pooled$lin_pred_probs[preds_pooled$package == 8]

# GFW probabilty owned by gov; non Anonymous (info = 1), SOS (sos = 1), government (own = 3)
add_gov_GFW <- preds_pooled$lin_pred_probs[preds_pooled$package == 2]

# GFW probabilty owned by ind; non Anonymous (info = 1), SOS (sos = 1), industry (own = 2)
add_ind_GFW <- preds_pooled$lin_pred_probs[preds_pooled$package == 13]

# GFW probabilty owned by fish; non Anonymous (info = 1), SOS (sos = 1), fisher (own = 1)
add_fisher_GFW <- preds_pooled$lin_pred_probs[preds_pooled$package == 12]

### Adding anon to GFW status quo results in a 2.913529% increase
lin_pred_GFW_add_anon <- GFW_prob - add_anon_GFW

### adding no sos to GFW status quo results in a 51.47519% decrease
lin_pred_GFW_add_no_sos <- GFW_prob- add_no_sos_GFW

### adding government ownership to GFW status quo results in a 21.12957% increase
lin_pred_GFW_add_gov <-  GFW_prob - add_gov_GFW

### adding industry ownership to GFW status quo results in a 7.380583% decrease
lin_pred_GFW_add_ind <- GFW_prob - add_ind_GFW

### adding fisher ownership to GFW status quo results in a 20.86605% increase
lin_pred_GFW_add_fisher <- GFW_prob - add_fisher_GFW
```

**Make pooled predictions using fitted() probs and calculate marginal probabilities based off of the status quo and GFW tech**

```{r}
# the status quo probability; Anonymous (info = 0), No SOS (sos = 0), Owned by fishermen (own = 1)
(status_quo_fitted <- preds_pooled$probs[preds_pooled$package == 15])
#0.5214112

## Make status quo non-anonymous; Non-Anonymous (info = 1), No SOS (sos = 0), Owned by fishermen (own = 1)
add_non_anon_fitted <- preds_pooled$probs[preds_pooled$package == 3]
#0.7451011

## Make status quo with SOS; Anonymous (info = 0), SOS (sos = 1), Owned by fishermen (own = 1)
add_sos_fitted <- preds_pooled$probs[preds_pooled$package == 7]

## Make status quo own by ind; Anonymous (info = 0), no SOS (sos = 0), Owned by industry (own = 2)
add_own_by_ind_fitted <- preds_pooled$probs[preds_pooled$package == 10]

## Make status quo own by gov; Anonymous (info = 0), no SOS (sos = 0), Owned by government (own = 3)
add_own_by_gov_fitted <- preds_pooled$probs[preds_pooled$package == 6]

## Make status quo own by public; Anonymous (info = 0), no SOS (sos = 0), Owned by public (own = 4)
add_own_by_public_fitted <- preds_pooled$probs[preds_pooled$package == 5]

### Adding non anon to status quo results in a 1.4% decrease
fitted_add_non_anon <-  status_quo_fitted - add_non_anon_fitted

### adding sos to status quo results in a 40.2% increase
fitted_add_sos <- status_quo_fitted - add_sos_fitted

### adding industry ownership results in a 38.8% decrease
fitted_add_ind <- status_quo_fitted - add_own_by_ind_fitted

### adding government ownership results in a 44.156% increase
fitted_add_gov <- status_quo_fitted - add_own_by_gov_fitted

### adding public access results in a 26.93022% decrease
fitted_add_public <- status_quo_fitted - add_own_by_public_fitted



# the status quo GFW probability; Non-Anonymous (info = 1), SOS (sos = 1), Public access (own = 4)
GFW_prob_fitted <- preds_pooled$probs[preds_pooled$package == 11]
#0.91077

# GFW probabilty with anonymous; Anonymous (info = 0), SOS (sos = 1), Public (own = 4)
add_anon_GFW_fitted <- preds_pooled$probs[preds_pooled$package == 4]

# GFW probabilty with no SOS; non Anonymous (info = 1), no SOS (sos = 0), Public (own = 4)
add_no_sos_GFW_fitted <- preds_pooled$probs[preds_pooled$package == 8]

# GFW probabilty owned by gov; non Anonymous (info = 1), SOS (sos = 1), government (own = 3)
add_gov_GFW_fitted <- preds_pooled$probs[preds_pooled$package == 2]

# GFW probabilty owned by ind; non Anonymous (info = 1), SOS (sos = 1), industry (own = 2)
add_ind_GFW_fitted <- preds_pooled$probs[preds_pooled$package == 13]

# GFW probabilty owned by fish; non Anonymous (info = 1), SOS (sos = 1), fisher (own = 1)
add_fisher_GFW_fitted <- preds_pooled$probs[preds_pooled$package == 12]

### Adding anon to GFW status quo results in a 12.3255 decrease
fitted_GFW_add_anon <- GFW_prob_fitted - add_anon_GFW_fitted

### adding no sos to GFW status quo results in a 77.52181% decrease
fitted_GFW_add_no_sos <- GFW_prob_fitted - add_no_sos_GFW_fitted

### adding government ownership to GFW status quo results in a 6.8% increase
fitted_GFW_add_gov <- GFW_prob_fitted - add_gov_GFW_fitted

### adding industry ownership to GFW status quo results in a 51.748% decrease
fitted_GFW_add_ind <- GFW_prob_fitted - add_ind_GFW_fitted

### adding fisher ownership to GFW status quo results in a 2.7% decrease
fitted_GFW_add_fisher <- GFW_prob_fitted - add_fisher_GFW_fitted

```

**Combine mlogit marginal probs into a dataframe**
```{r}

comp_lin_pred <- -1*100*data.frame(lin_pred_add_non_anon, lin_pred_add_sos, lin_pred_add_ind, lin_pred_add_gov, lin_pred_add_public) %>%
  rename( "add_non_anon" = 1, "add_sos" = 2, "add_ind" = 3, "add_gov" = 4, "add_public" = 5) 
rownames(comp_lin_pred) <- "lin_pred"

comp_fitted <- -1*100*data.frame(fitted_add_non_anon, fitted_add_sos, fitted_add_ind, fitted_add_gov, fitted_add_public) %>%
  rename( "add_non_anon" = 1, "add_sos" = 2, "add_ind" = 3, "add_gov" = 4, "add_public" = 5)
rownames(comp_fitted) <- "fitted"

comp_lin_pred_gfw <- -1*100*data.frame(lin_pred_GFW_add_anon, lin_pred_GFW_add_no_sos, lin_pred_GFW_add_anon, lin_pred_GFW_add_ind, lin_pred_GFW_add_gov) %>%
  rename( "gfw_add_anon" = 1, "gfw_add_no_sos" = 2, "gfw_add_fisher" = 3, "gfw_add_ind" = 4, "gfw_add_gov" = 5) 
rownames(comp_lin_pred_gfw) <- "lin_pred"

comp_gfw_fitted <- -1*100*data.frame(fitted_GFW_add_anon, fitted_GFW_add_no_sos, fitted_GFW_add_anon, fitted_GFW_add_ind, fitted_GFW_add_gov) %>%
  rename( "gfw_add_anon" = 1, "gfw_add_no_sos" = 2, "gfw_add_fisher" = 3, "gfw_add_ind" = 4, "gfw_add_gov" = 5) 
rownames(comp_gfw_fitted) <- "fitted"

final_reg <- rbind(comp_lin_pred, comp_fitted)

final_gfw <- rbind(comp_lin_pred_gfw, comp_gfw_fitted)

final_combined_mlogit_marg_probs <- cbind(final_reg, final_gfw)

write.csv(final_combined_mlogit_marg_probs, "output/unformatted_mlogit_pooled_marg_probs.csv", row.names = TRUE)
```








