---
title: "Hypothetical Village Data"
author: "Gage Clawson"
date: "1/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mefa)
library(survival)
library(utils)
library(cowplot)
library(WDI)
library(beepr)

total_sim_data <- read_csv("output/lm_15_allcombo_predictions.csv") %>%
  select(-X1)

set.seed(6969)

```

```{r}
# load necessary packages for importing the function
library(RCurl)
 
# import the function from repository
url_robust <- "https://raw.githubusercontent.com/IsidoreBeautrelet/economictheoryblog/master/robust_summary.R"
eval(parse(text = getURL(url_robust, ssl.verifypeer = FALSE)))
```

Puerto San Carlos; Based off of Jumbo Squid Fishery.
Paper: [Socioeconomic Diagnosis of the 2010 Jumbo Squid Artisanal Fishery near Magdalena Bay, Baja California Sur, Mexico](http://www.scielo.org.mx/scielo.php?script=sci_arttext&pid=S0188-88972014000100002)

Statistics: 
 - Population 5538 (2010 census data)
 - Artisanal Fisheries employ about 50% of the working population. 
 - 1800 fishing permits for jumbo squid 
   - "almost all of our respondents engage in other fisheries when jumbo squid are not present"
   - Assume that there are 1800 fishers in Puerto San Carlos. 
 - Average age is 34 years with a range of 18 to 78. 
 - No formal education (34%); formal (middle or high school; 30% + 33% = 63%); classify the remaining as higher (3%)
 - average of $11,090 Mexican Pesos each month (+/- $1,000 USD per month)
 - Assume biggest problem for the fishery is IUU. 
 - 8% did not have fishing communication technology on their boat. 

```{r}

# fishtech_yes <- 1800*0.92
# fishtech_no <- 1800*0.08
# 
# no_formal_edu <- 1800*0.34
# formal_edu <- 1800*0.63
# higher_edu <- 1800*0.03
# 
# iuu <- 1800
# 
# psc_filter <- total_sim_data %>%
#   filter(rank_one == "iuu", sos == 1, info == 0, own == 1)
wtpmin <- -5.35

fishtech <- c(0,1)
psc_prob_fishtech <- c(0.08, 0.92)
rank_one <- c("corruption", "pollution", "weather", "iuu")
education <- c("no_formal", "formal", "higher")
psc_prob_edu <- c(0.34, 0.63, 0.03)

gdp_prop_PSC_1 <- read_csv("../int/log_log_variables.csv") %>%
  filter(community == "PSC") 

gdp_prop_population <- length(gdp_prop_PSC_1$survey_id)

gdp_prop_prob <- gdp_prop_PSC_1 %>%
  group_by(gdp_prop) %>%
  summarise(n = length(gdp_prop)) %>% 
  mutate(prob = n/gdp_prop_population) %>%
  mutate(percent = round(prob*100))
gdp_prop_prob$percent[[1]] <- 5

gdp_prop_prob_new <- gdp_prop_prob %>%
  mutate(new_prob = percent/100) 


gdp_prop_PSC <- c(gdp_prop_prob_new$gdp_prop)
gdp_prop_prob_PSC <- c(gdp_prop_prob_new$new_prob)

psc <- data.frame(
                  fishtech = sample(rep(fishtech, round(1800*psc_prob_fishtech))),
                  education = sample(rep(education, round(1800*psc_prob_edu))),
                  rank_one = "iuu",
                  gdp_prop = sample(rep(gdp_prop_PSC, round(1800*gdp_prop_prob_PSC)))
                  )


## Try it with the gamma distribution from the paper ##

# ## Check the distribution of gdp_prop in our sample.
# gdp_prop_distribution <-gdp_prop_PSC_1 %>%
#   select(gdp_prop) %>%
#   gather(variable, value)
# 
# gdp_prop_distribution %>%
#  ggplot(aes(x = value, fill = variable)) +
#     geom_bkde() +
#     geom_rug() ## Gamma Distribution
# 
# 
# ## 11,090 Mexican Pesos/month = $590.83
# avg_income <- 590.83*12 #7089.96/year
# avg_income_lower <- (590.83 - 1000)*12
# avg_income_higher <- (590.83 + 1000)*12
# lambda_hat <- avg_income/12000^2
# alpha_hat <- avg_income^2/12000^2
# 
# x.gam <- rgamma(1800, rate = lambda_hat, shape = alpha_hat)
# 
# gdp_raw <- WDI(indicator = "NY.GDP.PCAP.KD", country=c("MX"), start = 2018, end = 2018) %>%
#   mutate(country = ifelse(country=="Mexico", "MEX", "IND")) %>%
#   rename(c = 1) %>%
#   select(-c, -year)
# 
# gdp_prop_psc_test <- x.gam/gdp_raw$NY.GDP.PCAP.KD
# hist(gdp_prop_psc_test)
# 
# psc <- data.frame(
#                   fishtech = sample(rep(fishtech, round(1800*psc_prob_fishtech))),
#                   education = sample(rep(education, round(1800*psc_prob_edu))),
#                   rank_one = "iuu",
#                   gdp_prop = gdp_prop_psc_test
#                   )



length(psc$fishtech[psc$fishtech ==0]) # this should be 144
length(psc$fishtech[psc$fishtech ==1])

length(psc$education[psc$education == "no_formal"])
length(psc$education[psc$education == "formal"])
length(psc$education[psc$education == "higher"])

length(psc$rank_one[psc$rank_one == "iuu"])



sos <- c(0,1)
info <- c(0,1)
own <- c("1", "2", "3", "4")

packages <- expand.grid(sos = sos,info = info, own= own)

#### Check
# new <- merge(psc,packages)
# new_filter <- new %>%
#   filter(sos == 1, info == 0, own == 1)
# 
# length(new_filter$education[new_filter$education == "no_formal"]) #612
# length(psc$rank_one[psc$rank_one == "iuu"]) #1800
# length(psc$fishtech[psc$fishtech == 1]) #1656
# ## IT WORKS!! 


psc_all_packages <- merge(psc, packages)

#write.csv(psc_all_packages, "hypo_village_data/PuertoSanCarlos/PuertoSanCarlos.csv", row.names = FALSE)

## load in specific model 
load("output/lm_15.rda")
load("../output/int_15.rda")
load("output/hicksian.rda")

## If using lm_15 (without gdp_prop), plug in this:
psc_all_packages_lm15 <- psc_all_packages %>%
  dplyr::select(-gdp_prop)

## If using lm with gdp_prop, plug in psc_all_packages... skip to below this, section labeled "GDP Prop Predictions"

psc_predict <- data.frame(psc_all_packages_lm15, lm_15_wtp = exp(predict(wtp_lm_15, newdata = psc_all_packages)) - 1 + wtpmin, int_15_wtp = predict(int_15, newdata = psc_all_packages)) ## if you want to add predictions from another model, just tack it onto the end. Now we can filter for a technology and make graphs based off of that. 

psc_predict <- data.frame(psc_all_packages_lm15, int_15_wtp = predict(int_15, newdata = psc_all_packages))

packages <- read_csv("../raw/packages.csv")  %>%
  filter(package <= 16) %>%
  mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,0,1)) %>%
  mutate(own = factor(own))

psc_predict_packages <- left_join(psc_predict, packages) 
#write.csv(psc_predict_packages, "hypo_village_data/PuertoSanCarlos/PuertoSanCarlos_predictions.csv", row.names = FALSE)

## Make a list of data frames for each package combination. 
my_data_psc <- list()
for (i in unique(psc_predict_packages$package)) {
    my_data_psc[[i]] <- filter(psc_predict_packages, package == i)
}

#save(my_data_psc, file="hypo_village_data/PuertoSanCarlos/psc_predict_by_package.RData") ## save this list to read back in for graphs.


```

```{r}

# read list in to begin making data usable to graph
load("hypo_village_data/PuertoSanCarlos/psc_predict_by_package.RData")

mean(my_data_psc[[1]]$lm_15_wtp)
mean(my_data_psc[[1]]$int_15_wtp)

test <- my_data_psc[[1]] ## this is psc with package 1 predictions. Can do the same for all 16 packages.

sim_total <- nrow(my_data_psc[[1]])
dollar_values <- seq(-3, 8, by = 0.01)

# test_hicksianxx <- psc_predict_packages %>%
#   filter(package == 1) %>%
#   merge(dollar_values) %>%
#   rename("bid" = "y") %>%
#   select(-lm_15_wtp, -int_15_wtp, -package)
# 
# predict_hicksian <- data.frame(test_hicksianxx, predict_prob <- predict(mylogit, newdata = test_hicksianxx, type = "response"))
# 
# ggplot(predict_hicksian, aes(x = bid, y = predict_prob)) + 
#   geom_point()

# Log Model Graph Data ## -- We are not using this anymore.
system.time(new_data_log <- lapply(my_data_psc, function(x) {

  graph_df <- x %>%
  merge(dollar_values) %>%
  mutate(opt_in_log = ifelse(lm_15_wtp > y, 1, 0 )) %>% ## if the wtp is greater than payment value, then they will opt in, otherwise, opt out
  arrange(opt_in_log)

group_df_opt_in <- graph_df %>%
  group_by(y, opt_in_log) %>%
  tally() %>%
  filter(opt_in_log == 1) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt In") %>% ##384 total scenarios
  ungroup()


group_df_opt_out <- graph_df %>%
  group_by(y, opt_in_log) %>%
  tally() %>%
  filter(opt_in_log == 0) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt Out") %>% ##384 total scenarios
  ungroup()

log_df <- rbind(group_df_opt_in, group_df_opt_out)

}))
beep()

save(new_data_log, file="hypo_village_data/PuertoSanCarlos/psc_predict_log_graphdata.RData")

## Interval Model Graph Data ##
system.time(new_data_int <- lapply(my_data_psc, function(x) {
  
  graph_df <- x %>%
  merge(dollar_values) %>%
  mutate(opt_in_int = ifelse(int_15_wtp > y, 1, 0 )) %>% ## if the wtp is greater than payment value, then they will opt in, otherwise, opt out
  arrange(opt_in_int)

group_df_opt_in <- graph_df %>%
  group_by(y, opt_in_int) %>%
  tally() %>%
  filter(opt_in_int == 1) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt In") %>% ##384 total scenarios
  ungroup()

group_df_opt_out <- graph_df %>%
  group_by(y, opt_in_int) %>%
  tally() %>%
  filter(opt_in_int == 0) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt Out") %>% ##384 total scenarios
  ungroup()

int_df <- rbind(group_df_opt_in, group_df_opt_out)
  
}))
beep()

save(new_data_int, file="hypo_village_data/PuertoSanCarlos/psc_predict_int_graphdata.RData")

```

## GRAPHS!

```{r}
## plot log log acceptance rate ##
load(file="hypo_village_data/PuertoSanCarlos/psc_predict_log_graphdata.RData")

# ## Test graph log log 
# ggplot(new_data_log[[7]], aes(x = y, y = perc_opt_in_log)) +
#   geom_point() +
#   geom_line() +
#   labs(x = "Payment to Fisher ($/month)", y = "Percent opt in VMS Program", title = "All Technology and Demographic Combinations") +
#   theme_bw() +
#   scale_x_continuous(breaks = seq(-3,8, 1))

log_all <- bind_rows(new_data_log, .id = "package") %>%
  merge(packages) %>%
  rename(
         "opt" = "opt_in_log") %>%
  mutate(regression_type = "log_log",
         package = as.integer(package))

## plot interval regression acceptance rate ##
load(file="hypo_village_data/PuertoSanCarlos/psc_predict_int_graphdata.RData")

# ## Test graph interval
# ggplot(new_data_log[[7]], aes(x = y, y = perc_opt_in_log)) +
#   geom_point() +
#   geom_line() +
#   labs(x = "Fisher Payment ($/month)", y = "Percent opt in VMS Program", title = "Package 7 Puerto San Carlos") +
#   theme_bw() +
#   scale_x_continuous(breaks = seq(-3,8, 1))

int_all <- bind_rows(new_data_int, .id = "package") %>%
  merge(packages) %>%
  rename(
         "opt" = "opt_in_int") %>%
  mutate(regression_type = "interval",
         package = as.integer(package))

# ## test graph log log 
# log_all %>% 
#   filter(package == 1) %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() + 
#   facet_wrap(~package+opt_in_out)

# ## test graph interval
# int_all %>% 
#   filter(package == 1) %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() + 
#   facet_wrap(~package+opt_in_out)

PSC_all_predictions <- rbind(log_all, int_all)

## graph package 1 for interval regression
# PSC_all_predictions %>%
#   filter(package == 1, regression_type == "interval") %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() +
#   facet_wrap(~package+opt_in_out)
## it works.

## Save the final dataframe

#write.csv(PSC_all_predictions, "hypo_village_data/PuertoSanCarlos/psc_all_predictions_FINAL.csv", row.names = FALSE)

## save all of the graphs 


PSC_all_predictions <- read_csv("hypo_village_data/PuertoSanCarlos/psc_all_predictions_FINAL.csv")

for(i in unique(PSC_all_predictions$package)){
  for(j in unique(PSC_all_predictions$opt_in_out)){
    for(m in unique(PSC_all_predictions$regression_type)){

  p <- ggplot(data = filter(PSC_all_predictions, package == i, opt_in_out == j, regression_type == m), aes(x = y, y = perc)) +
    geom_point() + 
    geom_line() +
    labs(title = "Puerto San Carlos", x = "Fisher Payment ($/month)", y = paste("Percent", j, "VMS Program", sep = " "), caption = paste("Package", i)) +
    theme_classic() +
    scale_x_continuous(breaks = seq(-3,8, 1)) +
    scale_y_continuous(breaks = seq(0,1, 0.1))

  save_plot(p, file = paste0("hypo_village_data/PuertoSanCarlos/graphs/", m, "_", i, "_", j, ".png"))
  
    }
  }
}


# graph_data_psc <- PSC_all_predictions %>%
#   filter(opt_in_out == "Opt In", package %in% c(8,11), regression_type == "interval")

graph_data_psc <- PSC_all_predictions %>%
  filter(sos == 1, info == 0, own == 1, opt_in_out == "Opt In", regression_type == "interval")

ggplot(graph_data_psc, aes(x = y, y = perc)) + 
    geom_line() +
    theme_bw()

  
  ggplot(graph_data_psc, aes(x = y, y = perc, color = factor(sos))) + 
    geom_line() +
    theme_bw() +
    labs() +
    labs(x = "Cost to Fisher ($ per month)", y = "Proportion of Population to Opt In") +
    #geom_vline(xintercept = c(0.97, -0.21), linetype = "dotted", color = "darkgreen") +
     #geom_vline(xintercept = c(3.15, 4.41), linetype = "dotted", color = "red") +
        scale_x_continuous(breaks = c(-3,-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
    #theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    scale_color_manual(values = c("goldenrod1", "lightseagreen"), name = "SOS Functionality", labels = c("No", "Yes")) +
    scale_y_continuous(breaks = seq(0,1,0.2))
  #caption = "Technology Attributes: Non-anonymous, Public access \n Biggest problem: IUU"

```

GDP Prop Predictions

```{r}
## If using lm with gdp_prop, plug in psc_all_packages... skip to below this, section labeled "GDP Prop Predictions"

load("output/wtp_lm_16_gdp_prop.rda")
load("output/int_16_gdp_prop.rda")

psc_predict <- data.frame(psc_all_packages, lm_16_wtp = exp(predict(wtp_lm_16, newdata = psc_all_packages)) - 1 + wtpmin, int_16_wtp = predict(int_16, newdata = psc_all_packages)) ## if you want to add predictions from another model, just tack it onto the end. Now we can filter for a technology and make graphs based off of that. 
packages <- read_csv("raw/packages.csv")  %>%
  filter(package <= 16) %>%
  mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,0,1)) %>%
  mutate(own = factor(own))

psc_predict_packages <- left_join(psc_predict, packages) 

#write.csv(psc_predict_packages, "hypo_village_data/PuertoSanCarlos_gdp/PuertoSanCarlos_predictions_gdp.csv", row.names = FALSE)

## Make a list of data frames for each package combination. 
my_data_psc <- list()
for (i in unique(psc_predict_packages$package)) {
    my_data_psc[[i]] <- filter(psc_predict_packages, package == i)
}

#save(my_data_psc, file="hypo_village_data/PuertoSanCarlos_gdp/psc_predict_by_package_gdp.RData") ## save this list to read back in for graphs.


```

```{r}

# read list in to begin making data usable to graph
#load("hypo_village_data/PuertoSanCarlos/psc_predict_by_package.RData")

mean(my_data_psc[[1]]$lm_16_wtp)
mean(my_data_psc[[1]]$int_16_wtp)

test <- my_data_psc[[1]] ## this is psc with package 1 predictions. Can do the same for all 16 packages.

sim_total <- nrow(my_data_psc[[1]])
dollar_values <- seq(-3, 8, by = 0.01)

## Log Model Graph Data ##
system.time(new_data_log <- lapply(my_data_psc, function(x) {
  
  graph_df <- x %>%
  merge(dollar_values) %>%
  mutate(opt_in_log = ifelse(lm_16_wtp > y, 1, 0 )) %>% ## if the wtp is greater than payment value, then they will opt in, otherwise, opt out
  arrange(opt_in_log)

group_df_opt_in <- graph_df %>%
  group_by(y, opt_in_log) %>%
  tally() %>%
  filter(opt_in_log == 1) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt In") %>% ##384 total scenarios
  ungroup()
    

group_df_opt_out <- graph_df %>%
  group_by(y, opt_in_log) %>%
  tally() %>%
  filter(opt_in_log == 0) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt Out") %>% ##384 total scenarios
  ungroup()

log_df <- rbind(group_df_opt_in, group_df_opt_out)

}))
beep()

#save(new_data_log, file="hypo_village_data/PuertoSanCarlos_gdp/psc_predict_log_graphdata_gdp.RData")

## Interval Model Graph Data ##
system.time(new_data_int <- lapply(my_data_psc, function(x) {
  
  graph_df <- x %>%
  merge(dollar_values) %>%
  mutate(opt_in_int = ifelse(int_16_wtp > y, 1, 0 )) %>% ## if the wtp is greater than payment value, then they will opt in, otherwise, opt out
  arrange(opt_in_int)

group_df_opt_in <- graph_df %>%
  group_by(y, opt_in_int) %>%
  tally() %>%
  filter(opt_in_int == 1) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt In") %>% ##384 total scenarios
  ungroup()

group_df_opt_out <- graph_df %>%
  group_by(y, opt_in_int) %>%
  tally() %>%
  filter(opt_in_int == 0) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt Out") %>% ##384 total scenarios
  ungroup()

int_df <- rbind(group_df_opt_in, group_df_opt_out)
  
}))
beep()

#save(new_data_int, file="hypo_village_data/PuertoSanCarlos_gdp/psc_predict_int_graphdata_gdp.RData")

```

## GRAPHS!

```{r}
## plot log log acceptance rate ##
load(file="hypo_village_data/PuertoSanCarlos_gdp/psc_predict_log_graphdata_gdp.RData")

# ## Test graph log log 
# ggplot(new_data_log[[7]], aes(x = y, y = perc_opt_in_log)) +
#   geom_point() +
#   geom_line() +
#   labs(x = "Payment to Fisher ($/month)", y = "Percent opt in VMS Program", title = "All Technology and Demographic Combinations") +
#   theme_bw() +
#   scale_x_continuous(breaks = seq(-3,8, 1))

log_all <- bind_rows(new_data_log, .id = "package") %>%
  merge(packages) %>%
  rename(
         "opt" = "opt_in_log") %>%
  mutate(regression_type = "log_log",
         package = as.integer(package))

## plot interval regression acceptance rate ##
load(file="hypo_village_data/PuertoSanCarlos_gdp/psc_predict_int_graphdata_gdp.RData")

# ## Test graph interval
# ggplot(new_data_log[[7]], aes(x = y, y = perc_opt_in_log)) +
#   geom_point() +
#   geom_line() +
#   labs(x = "Fisher Payment ($/month)", y = "Percent opt in VMS Program", title = "Package 7 Puerto San Carlos") +
#   theme_bw() +
#   scale_x_continuous(breaks = seq(-3,8, 1))

int_all <- bind_rows(new_data_int, .id = "package") %>%
  merge(packages) %>%
  rename(
         "opt" = "opt_in_int") %>%
  mutate(regression_type = "interval",
         package = as.integer(package))

# ## test graph log log 
# log_all %>% 
#   filter(package == 1) %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() + 
#   facet_wrap(~package+opt_in_out)

# ## test graph interval
# int_all %>% 
#   filter(package == 1) %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() + 
#   facet_wrap(~package+opt_in_out)

PSC_all_predictions <- rbind(log_all, int_all)

## graph package 1 for interval regression
# PSC_all_predictions %>%
#   filter(package == 1, regression_type == "interval") %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() +
#   facet_wrap(~package+opt_in_out)
## it works.

## Save the final dataframe

#write.csv(PSC_all_predictions, "hypo_village_data/PuertoSanCarlos_gdp/psc_all_predictions_FINAL_gdp.csv", row.names = FALSE)

## save all of the graphs 


PSC_all_predictions <- read_csv("hypo_village_data/PuertoSanCarlos_gdp/psc_all_predictions_FINAL_gdp.csv")

for(i in unique(PSC_all_predictions$package)){
  for(j in unique(PSC_all_predictions$opt_in_out)){
    for(m in unique(PSC_all_predictions$regression_type)){

  p <- ggplot(data = filter(PSC_all_predictions, package == i, opt_in_out == j, regression_type == m), aes(x = y, y = perc)) +
    geom_line() +
    geom_point() +
    labs(title = "Puerto San Carlos", x = "Fisher Payment ($/month)", y = paste("Percent", j, "VMS Program", sep = " "), caption = paste("Package", i)) +
    theme_classic() +
    scale_x_continuous(breaks = seq(-3,8, 1)) +
    scale_y_continuous(breaks = seq(0,1, 0.1))

  save_plot(p, file = paste0("hypo_village_data/PuertoSanCarlos_gdp/graphs/", m, "_", i, "_", j, ".png"))
  
    }
  }
}

```

```{r}


try_psc<-psc_predict %>% 
  left_join(packages) %>% 
  #filter(regression_type == "interval") %>% 
  group_by(package, int_15_wtp) %>% 
  tally() %>% 
 # ungroup() %>% 
  mutate(prop=n/sum(n)) %>% 
  arrange(desc(int_15_wtp)) %>% 
  mutate(prop_sum = cumsum(prop)) 


ggplot(try_psc, aes(x= int_15_wtp)) +
  geom_smooth(aes(y=prop_sum, color=as.factor(package), fill = as.factor(package)), se = FALSE)

try_psc %>% 
  filter(package == 1) %>%
  ggplot( aes(x = int_15_wtp, y = prop_sum)) +
  geom_point()
```



Pepela Indonesia
Paper: 

Statistics: 
 - Population 370
 - No formal education (0.04864865); formal (0.9432432); classify the remaining as higher (0.008108108)
 - Assume biggest problem for the fishery is weather. 
 - 30% did not have fishing technology on their boat. 

```{r}
wtpmin <- -5.35

fishtech <- c(0,1)
pepela_prob_fishtech <- c(0.3, 0.7)
# rank_one <- c("corruption", "pollution", "weather", "iuu")
education <- c("no_formal", "formal", "higher")
pepela_prob_edu <- c(0.04864865, 0.9432432, 0.008108108)

pepela <- data.frame(
                  fishtech = sample(rep(fishtech, round(370*pepela_prob_fishtech))),
                  education = sample(rep(education, round(370*pepela_prob_edu))),
                  rank_one = "weather"
                  )



length(pepela$fishtech[pepela$fishtech ==0]) # this should be 111 
length(pepela$fishtech[pepela$fishtech ==1]) #259
 
length(pepela$education[pepela$education == "no_formal"]) # 18
length(pepela$education[pepela$education == "formal"]) # 349
length(pepela$education[pepela$education == "higher"]) # 3

length(pepela$rank_one[pepela$rank_one == "weather"]) # 370



sos <- c(0,1)
info <- c(0,1)
own <- c("1", "2", "3", "4")

packages <- expand.grid(sos = sos,info = info, own= own)

# new <- merge(psc,packages)
# new_filter <- new %>%
#   filter(sos == 1, info == 0, own == 1)
# 
# length(new_filter$education[new_filter$education == "no_formal"]) #612
# length(psc$rank_one[psc$rank_one == "iuu"]) #1800
# length(psc$fishtech[psc$fishtech == 1]) #1656
# ## IT WORKS!! 


pepela_all_packages <- merge(pepela, packages)

#write.csv(pepela_all_packages, "hypo_village_data/Pepela/pepela.csv", row.names = FALSE)

## load in specific model 
load("output/lm_15.rda")
load("output/int_15.rda")

pepela_predict <- data.frame(pepela_all_packages, lm_15_wtp = exp(predict(wtp_lm_15, newdata = pepela_all_packages)) - 1 + wtpmin, int_15_wtp = predict(int_15, newdata = pepela_all_packages)) ## if you want to add predictions from another model, just tack it onto the end. Now we can filter for a technology and make graphs based off of that. 

packages <- read_csv("raw/packages.csv")  %>%
  filter(package <= 16) %>%
  mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,0,1)) %>%
  mutate(own = factor(own))

pepela_predict_packages <- left_join(pepela_predict, packages) 
#write.csv(pepela_predict_packages, "hypo_village_data/Pepela/pepela_predictions.csv", row.names = FALSE)

## Make a list of data frames for each package combination. 
my_data_pepela <- list()
for (i in unique(pepela_predict_packages$package)) {
    my_data_pepela[[i]] <- filter(pepela_predict_packages, package == i)
}

#save(my_data_pepela, file="hypo_village_data/Pepela/pepela_predict_by_package.RData") ## save this list to read back in for graphs.

try_p<-pepela_predict_packages %>% 
#  filter(package==1) %>% 
  group_by(package, int_15_wtp) %>% 
  tally() %>% 
 # ungroup() %>% 
  mutate(prop=n/sum(n)) %>% 
  arrange(desc(int_15_wtp)) %>% 
  mutate(prop_sum = cumsum(prop)) 


ggplot(try_p, aes(x= int_15_wtp)) +
  geom_smooth(aes(y=prop_sum, color=as.factor(package), fill = as.factor(package)))

```

```{r}

# read list in to begin making data usable to graph
load("hypo_village_data/Pepela/pepela_predict_by_package.RData")

mean(my_data_pepela[[1]]$lm_15_wtp)
mean(my_data_pepela[[1]]$int_15_wtp)

test <- my_data_pepela[[1]] ## this is psc with package 1 predictions. Can do the same for all 16 packages.

sim_total <- nrow(my_data_pepela[[1]])
dollar_values <- seq(-3, 8, by = 0.01)

## Log Model Graph Data ##
system.time(new_data_log <- lapply(my_data_pepela, function(x) {
  
  graph_df <- x %>%
  merge(dollar_values) %>%
  mutate(opt_in_log = ifelse(lm_15_wtp > y, 1, 0 )) %>% ## if the wtp is greater than payment value, then they will opt in, otherwise, opt out
  arrange(opt_in_log)

group_df_opt_in <- graph_df %>%
  group_by(y, opt_in_log) %>%
  tally() %>%
  filter(opt_in_log == 1) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt In") %>% ##384 total scenarios
  ungroup()
    

group_df_opt_out <- graph_df %>%
  group_by(y, opt_in_log) %>%
  tally() %>%
  filter(opt_in_log == 0) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt Out") %>% ##384 total scenarios
  ungroup()

log_df <- rbind(group_df_opt_in, group_df_opt_out)

}))
beep()

#save(new_data_log, file="hypo_village_data/Pepela/pepela_predict_log_graphdata.RData")

## Interval Model Graph Data ##
system.time(new_data_int <- lapply(my_data_pepela, function(x) {
  
  graph_df <- x %>%
  merge(dollar_values) %>%
  mutate(opt_in_int = ifelse(int_15_wtp > y, 1, 0 )) %>% ## if the wtp is greater than payment value, then they will opt in, otherwise, opt out
  arrange(opt_in_int)

group_df_opt_in <- graph_df %>%
  group_by(y, opt_in_int) %>%
  tally() %>%
  filter(opt_in_int == 1) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt In") %>% ##384 total scenarios
  ungroup()

group_df_opt_out <- graph_df %>%
  group_by(y, opt_in_int) %>%
  tally() %>%
  filter(opt_in_int == 0) %>% ## filter for all opt ins...
  mutate(perc = n/sim_total,
         opt_in_out = "Opt Out") %>% ##384 total scenarios
  ungroup()

int_df <- rbind(group_df_opt_in, group_df_opt_out)
  
}))
beep()

#save(new_data_int, file="hypo_village_data/Pepela/pepela_predict_int_graphdata.RData")

```

## GRAPHS!

```{r}
## plot log log acceptance rate ##
load(file="hypo_village_data/Pepela/pepela_predict_log_graphdata.RData")

# ## Test graph log log 
# ggplot(new_data_log[[7]], aes(x = y, y = perc_opt_in_log)) +
#   geom_point() +
#   geom_line() +
#   labs(x = "Payment to Fisher ($/month)", y = "Percent opt in VMS Program", title = "All Technology and Demographic Combinations") +
#   theme_bw() +
#   scale_x_continuous(breaks = seq(-3,8, 1))

log_all <- bind_rows(new_data_log, .id = "package") %>%
  merge(packages) %>%
  rename(
         "opt" = "opt_in_log") %>%
  mutate(regression_type = "log_log",
         package = as.integer(package))

## plot interval regression acceptance rate ##
load(file="hypo_village_data/Pepela/pepela_predict_int_graphdata.RData")

# ## Test graph interval
# ggplot(new_data_log[[7]], aes(x = y, y = perc_opt_in_log)) +
#   geom_point() +
#   geom_line() +
#   labs(x = "Fisher Payment ($/month)", y = "Percent opt in VMS Program", title = "Package 7 Puerto San Carlos") +
#   theme_bw() +
#   scale_x_continuous(breaks = seq(-3,8, 1))

int_all <- bind_rows(new_data_int, .id = "package") %>%
  merge(packages) %>%
  rename(
         "opt" = "opt_in_int") %>%
  mutate(regression_type = "interval",
         package = as.integer(package))

# ## test graph log log 
# log_all %>% 
#   filter(package == 1) %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() + 
#   facet_wrap(~package+opt_in_out)

# ## test graph interval
# int_all %>% 
#   filter(package == 1) %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() + 
#   facet_wrap(~package+opt_in_out)

Pepela_all_predictions <- rbind(log_all, int_all)

## graph package 1 for interval regression
# PSC_all_predictions %>%
#   filter(package == 1, regression_type == "interval") %>%
#   ggplot(aes(x = y, y = perc)) +
#   geom_point() +
#   geom_line() +
#   facet_wrap(~package+opt_in_out)
## it works.

## Save the final dataframe

#write.csv(Pepela_all_predictions, "hypo_village_data/Pepela/pepela_all_predictions_FINAL.csv", row.names = FALSE)

## save all of the graphs 


Pepela_all_predictions <- read_csv("hypo_village_data/Pepela/pepela_all_predictions_FINAL.csv")

for(i in unique(Pepela_all_predictions$package)){
  for(j in unique(Pepela_all_predictions$opt_in_out)){
    for(m in unique(Pepela_all_predictions$regression_type)){

  p <- ggplot(data = filter(Pepela_all_predictions, package == i, opt_in_out == j, regression_type == m), aes(x = y, y = perc)) +
    geom_point() + 
    geom_line() +
    labs(title = "Pepela", x = "Fisher Payment ($/month)", y = paste("Percent", j, "VMS Program", sep = " "), caption = paste("Package", i)) +
    theme_classic() +
    scale_x_continuous(breaks = seq(-3,8, 1)) +
    scale_y_continuous(breaks = seq(0,1, 0.1))

  save_plot(p, file = paste0("hypo_village_data/Pepela/graphs/", m, "_", i, "_", j, ".png"))
  
    }
  }
}

graph_data_pepela <- Pepela_all_predictions %>%
  filter(opt_in_out == "Opt In", package %in% c(8,11), regression_type == "interval")
  
  ggplot(graph_data_pepela, aes(x = y, y = perc, color = factor(sos))) + 
    geom_line() +
    theme_bw() +
    #labs(caption = "Non-anonymous, Public access") +
    labs(x = "Cost to Fisher ($ per month)", y = "Proportion of Population to Opt In") +
    #geom_vline(xintercept = c(-1.88, -0.61), linetype = "dotted", color = "darkgreen") +
     #geom_vline(xintercept = c(3.15, 4.41), linetype = "dotted", color = "red") +
        scale_x_continuous(breaks = c(-3,-2, -1, 0, 1, 2,3 ,4)) +
    #theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    scale_color_manual(values = c("goldenrod1", "lightseagreen"), name = "SOS Functionality", labels = c("No", "Yes"))  +
    scale_y_continuous(breaks = seq(0,1, 0.2))
       # scale_color_discrete(name = "SOS Functionality", labels = c("No", "Yes")) 

```

