---
title: "clogit"
output: html_document
---

## Summary
Running Conditional Logit Analysis on the following models to compare output and explore potential bias; Standard opt-out model (Model I), Pooled (Model II), Unforced Responses (Model III), and Forced Responses (Model IV).
 
## Data Source 
Personal Interviews
 
## Reference 
Panga Watch
 
## Downloaded
October 21, 2019
 
Time range: 
2019
 
## Format
comma separated values

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(survival)
library(AlgDesign)
library(DT)
library(stargazer)
library(xtable)
library(here)
library(kableExtra)
#library("mlogit")
```

Standard opt-out model (Model I)
```{r}
standard_opt_out <- read_csv("int/standard_opt_out_fix.csv") %>% 
  mutate(own.fisher=ifelse(own==1,1,0), own.industry=ifelse(own==2,1,0), own.gov=ifelse(own==3,1,0), own.public=ifelse(own==4,1,0))


standard_clogit<-clogit(RES~ASC+sos+info+own.fisher+own.industry+own.gov+own.public+strata(STR), data=standard_opt_out)
standard_clogit
```

Pooled (Model II)
```{r}
pooled <- read_csv("int/pooled_data.csv")%>% 
  mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,1,0)) %>%
  mutate(own.fisher=ifelse(own==1,1,0), own.industry=ifelse(own==2,1,0), own.gov=ifelse(own==3,1,0), own.public=ifelse(own==4,1,0))


pooled_clogit<-clogit(RES~sos+info+own.fisher+own.industry+own.gov+own.public+strata(STR), data=pooled)
pooled_clogit
```

Unforced Responses (Model III)
```{r}
unforced <- read_csv("int/unforced_data.csv")%>% 
  mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,1,0)) %>%
  mutate(own.fisher=ifelse(own==1,1,0), own.industry=ifelse(own==2,1,0), own.gov=ifelse(own==3,1,0), own.public=ifelse(own==4,1,0))

unforced_clogit<-clogit(RES~sos+info+own.fisher+own.industry+own.gov+own.public+strata(STR), data=unforced)
unforced_clogit
```

Forced Responses (Model IV)
```{r}
forced <- read_csv("int/forced_data.csv")%>% 
  mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,1,0)) %>%
  mutate(own.fisher=ifelse(own==1,1,0), own.industry=ifelse(own==2,1,0), own.gov=ifelse(own==3,1,0), own.public=ifelse(own==4,1,0))

forced_clogit<-clogit(RES~sos+info+own.fisher+own.industry+own.gov+own.public+strata(STR), data=forced)
summary(forced_clogit)
```

```{r}
standard_clogit
pooled_clogit
unforced_clogit
forced_clogit
```
```{r}
#pooled= 144.3
#unforced = 148.5
#forced = 13.73

#(-2(144.3-(148.5+13.73)))
#35.68
```

